### 2017-06-16 manuscript.Rmd
Start manuscript draft

---
title: "Manuscript"
author: "Nico Boyd, Greg Macfarlane, Kari Watkins"
date: "6/16/2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup}
library(geojsonio)
library(leaflet)
```

# Abstract

## Introduction

This research will identify the correlation between size and access to urban parks, and physical activity, obesity and mental health at the neighborhood level. Proximity to parks is associated with increased physical activity and reduced obesity, but little research has been conducted on the relationship between accessibility to parks and health outcomes.

## Methods
Using data for three urban areas, we created a new measure for access to parks called park choice accessibility. Park choice accessibility uses a gravity model to interact distance to parks and quality of those parks as defined by size and amenities. A small park very close to a neighborhood can have a major impact, but a larger park at a similar distance may have an even larger impact. Similarly, a large park can be further away and still have an impact on health outcomes. Using spatial regression analysis, we are assessing whether park choice accessibility is associated with increased physical activity or decreased prevalence of obesity at the neighborhood level. The analysis controls for socioeconomic covariates such as age, marital status, income, and educational attainment.

##
Our anticipated results will assess the difference in physical activity and obesity at the neighborhood level when comparing proximity to parks and access to parks of various sizes and qualities as defined by park choice accessibility. We hope to make progress in achieving the Healthy People 2020 goals on physical activity, reduced sedentary behavior, and building healthy communities.

# Background/Literature Review

# Methods

```{r load_data}
denver_tracts <- geojson_read("data/denver_tracts.geojson", what = "sp")

```

# Results

# Discussion

# Conclusion

### 2017-06-16 manuscript.Rmd
Added Dave Ederer as a co-author

@@
 title: "Manuscript"
-author: "Nico Boyd, Greg Macfarlane, Kari Watkins"
+author: "Nico Boyd, Greg Macfarlane, Kari Watkins, Dave Ederer"
 date: "6/16/2017"

### 2017-06-16 manuscript.Rmd
Converted and loaded in the five remaining geojson files

@@
 denver_tracts <- geojson_read("data/denver_tracts.geojson", what = "sp")
+denver_parks <- geojson_read ("data/denver_parks.geojson", what = "sp")
 
+boston_tracts <- geojson_read("data/boston_tracts.geojson", what = "sp")
+boston_parks <- geojson_read("data/boston_parks.geojson", what = "sp")
+
+nyc_tracts <- geojson_read("data/nyc_tracts.geojson", what = "sp")
+nyc_parks <- geojson_read("data/nyc_parks.geojson", what = "sp")
 ```

### 2017-06-19 R/LogLikelihood_Comparison.Rmd
Comparison tables for the log likelihood values

---
title: "Comparison of Log Likelihood Values"
author: "Nico Boyd"
date: "June 19, 2017"
output:
  html_document: default
---

```{r set-options, echo=FALSE, cache=FALSE}
options(width=120)
```

Greg - below I've created a table for each of our cities that compares the log likelilhood values between models. Something I found interesting was the fact that when park access is added into the models, the log likelihood values are the same for the physical activity and mental health models. Does this strike you as odd?

Also, quick question about model selection: since the log likelihood values are all negative, should I or should I not select the final models based on the highest **ABSOLUTE VALUE** of the log likelihood? If we're not selecting models based on absolute value, each city has two clear winners:

  * Denver: models 1 & 4 (both equally likely)
  * Boston: models 3 & 6 (both equally likely)
  * NYC: models 1 & 2 (both equally likely)

```{r denver_models, echo=FALSE}

Denver_Loglikelihoods <- data.frame(row.names=paste("Denver",1:6))
Denver_Loglikelihoods[,1] <- c(-184.46, -184.46, -184.46, -184.46, -184.46, -184.46)
Denver_Loglikelihoods[,2] <- c(-218.96, -218.96, -218.96, -218.96, -218.96, -218.96)
Denver_Loglikelihoods[,3] <- c(-218.96, -218.96, -218.96, -218.96, -218.96, -218.96)
Denver_Loglikelihoods[,4] <- c(-184.39, -184.43, -184.43, -184.39, -184.43, -184.43)
Denver_Loglikelihoods[,5] <- c(-218.06, -218.28, -218.31, -218.06, -218.28, -218.31)
Denver_Loglikelihoods[,6] <- c(-218.06, -218.28, -218.31, -218.06, -218.28, -218.31)
colnames(Denver_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")

Denver_Loglikelihoods
```

```{r boston_models, echo=FALSE}

Boston_Loglikelihoods <- data.frame(row.names=paste("Boston",1:6))
Boston_Loglikelihoods[,1] <- c(-258.16, -258.16, -258.16, -258.16, -258.16, -258.16)
Boston_Loglikelihoods[,2] <- c(-312.80, -312.80, -312.80, -312.80, -312.80, -312.80)
Boston_Loglikelihoods[,3] <- c(-312.80, -312.80, -312.80, -312.80, -312.80, -312.80)
Boston_Loglikelihoods[,4] <- c(-258.16, -258.16, -258.15, -258.16, -258.16, -258.15)
Boston_Loglikelihoods[,5] <- c(-312.80, -312.79, -312.79, -312.80, -312.79, -312.79)
Boston_Loglikelihoods[,6] <- c(-312.80, -312.79, -312.79, -312.80, -312.79, -312.79)
colnames(Boston_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")

Boston_Loglikelihoods
```

```{r nyc_models, echo=FALSE}

NYC_Loglikelihoods <- data.frame(row.names=paste("NYC   ",1:3))
NYC_Loglikelihoods[,1] <- c(-3929.85, -3929.85, -3929.85)
NYC_Loglikelihoods[,2] <- c(-4421.83, -4421.83, -4421.83)
NYC_Loglikelihoods[,3] <- c(-4421.83, -4421.83, -4421.83)
NYC_Loglikelihoods[,4] <- c(-3929.14, -3929.14, -3929.36)
NYC_Loglikelihoods[,5] <- c(-4421.80, -4421.80, -4421.82)
NYC_Loglikelihoods[,6] <- c(-4421.80, -4421.80, -4421.82)
colnames(NYC_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")

NYC_Loglikelihoods
```

### 2017-06-26 manuscript.Rmd
Added geojson files to the manuscript
Added Denver 'results' section and calculated impacts of Denver SDM models.

@@
 library(geojsonio)
+library(leaflet)
+library(tidyverse)
+library(spdep)
+library(maptools)
+library(rgdal)
+library(rgeos)
+library(texreg)
 library(leaflet)
@@
 
+## Denver
+
+Load Denver geospatial data (tracts and parks):
+```{r denver_data}
+tracts <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_Final") 
+plot(tracts)
+
+parks <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_All_Parks") 
+plot(parks)
+```
+
+Transform the attribute table into a tibble and select the relevant variables:
+```{r show_denverdata}
+tracts@data <- tbl_df(tracts@data) %>%
+  select(GEOID_TRAC, OBESITY, Park_Percent, PhysAct, MENTAL, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegePercent, Pct0to17, Pct18to29, Pct30to64, Pct65plus, SinglePercent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic) %>%
+    mutate_each(funs(ifelse(is.na(.), 0, .)), Park_Percent)
+tracts@data
+```
+
+Calculate the logsum given a tracts and parks dataset:
+```{r denver_accessibility}
+source('R/size00001dist5.R', echo=TRUE)
+tracts$park_ls <- calculate_park_logsums(tracts, parks, betas = c(.00001, -5))
+```
+
+Create regression equations for use in spatial econometric models:
+```{r denver_equations}
+denver_base_formula <- formula(~Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + CollegePercent + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + PctOther + PctHispanic)
+
+denver_parks_formula <- update(base_formula, . ~ . + park_ls)
+```
+
+Locate the centroid of all parks and all census tracts and create a distance matrix:
+```{r denver_distancematrix}
+tract_centroids <- gCentroid(tracts, byid = TRUE) #if byid = FALSE, then centroid of "all" points
+park_centroids <- gCentroid(parks, byid = TRUE)
+distance_matrix <- gDistance(tract_centroids, park_centroids, byid = TRUE)
+dim(distance_matrix)
+```
+
+Create a spatial weights matrix:
+```{r denver_W}
+neighbors <- poly2nb(tracts, queen = FALSE)
+W <- nb2listw(neighbours = neighbors, zero.policy = TRUE)
+print(W, zero.policy = TRUE)
+```
+
+Estimate spatial econometric models for the `OBESITY` variable. The first model of each different type does not include `park_ls`:
+```{r denver_spmodels_obesity}
+denver_obese_sem <- errorsarlm(update(denver_base_formula, OBESITY ~ .), data = tracts@data, 
+                      listw = W, zero.policy = TRUE)
+denver_obese_sem2 <- errorsarlm(update(denver_parks_formula, OBESITY ~ .), data = tracts@data, 
+                      listw = W, zero.policy = TRUE)
+denver_obese_sdm <- lagsarlm(update(denver_base_formula, OBESITY ~ .), data = tracts@data, 
+                      listw = W, zero.policy = TRUE, type = "mixed")
+denver_obese_sdm2 <- lagsarlm(update(denver_parks_formula, OBESITY ~ .), data = tracts@data, 
+                      listw = W, zero.policy = TRUE, type = "mixed")
+```
+
+Estimate spatial econometric models for the `PhysAct` variable. The first model of each different type does not include `park_ls`:
+```{r denver_spmodels_physact}
+denver_physact_sem <- errorsarlm(update(denver_base_formula, PhysAct ~ .), data = tracts@data, 
+                          listw = W, zero.policy = TRUE)
+denver_physact_sem2 <- errorsarlm(update(denver_parks_formula, PhysAct ~ .), 
+                           data = tracts@data, listw = W, zero.policy = TRUE)
+denver_physact_sdm <- lagsarlm(update(denver_base_formula, PhysAct ~ .), data = tracts@data, 
+                        listw = W, zero.policy = TRUE, type = "mixed")
+denver_physact_sdm2 <- lagsarlm(update(denver_parks_formula, PhysAct ~ .), data = tracts@data,
+                         listw = W, zero.policy = TRUE, type = "mixed")
+```
+
+Estimate spatial econometric models for the `MENTAL` variable. The first model of each different type does not include `park_ls`:
+```{r denver_spmodels_mental}
+denver_mental_sem <- errorsarlm(update(denver_base_formula, MENTAL ~ .), data = tracts@data, 
+                          listw = W, zero.policy = TRUE)
+denver_mental_sem2 <- errorsarlm(update(denver_parks_formula, MENTAL ~ .), 
+                           data = tracts@data, listw = W, zero.policy = TRUE)
+denver_mental_sdm <- lagsarlm(update(denver_base_formula, MENTAL ~ .), data = tracts@data, 
+                        listw = W, zero.policy = TRUE, type = "mixed")
+denver_mental_sdm2 <- lagsarlm(update(denver_parks_formula, MENTAL ~ .), data = tracts@data,
+                         listw = W, zero.policy = TRUE, type = "mixed")
+```
+
+Calculate the impacts of the spatial durbin models:
+```{r denverSDM_impacts}
+listw <- as(W, "CsparseMatrix")
+tr_mult <- trW(listw, type="mult")
+tr_MC <- trW(listw, type="MC")
+set.seed(1)
+
+denver_noparks_obesemult <- impacts(denver_obese_sdm, tr=tr_mult)
+denver_parks_obesemult <- impacts(denver_obese_sdm2, tr=tr_mult)
+denver_noparks_obeseMC <- impacts(denver_obese_sdm, tr=tr_MC)
+denver_parks_obeseMC <- impacts(denver_obese_sdm2, tr=tr_MC)
+
+denver_noparks_physactmult <- impacts(denver_physact_sdm, tr=tr_mult)
+denver_parks_physactmult <- impacts(denver_physact_sdm2, tr=tr_mult)
+denver_noparks_physactMC <- impacts(denver_physact_sdm, tr=tr_MC)
+denver_parks_physactMC <- impacts(denver_physact_sdm2, tr=tr_MC)
+
+denver_noparks_mentalmult <- impacts(denver_mental_sdm, tr=tr_mult)
+denver_parks_mentalmult <- impacts(denver_mental_sdm2, tr=tr_mult)
+denver_noparks_mentalMC <- impacts(denver_mental_sdm, tr=tr_MC)
+denver_parks_mentalMC <- impacts(denver_mental_sdm2, tr=tr_MC)
+```
+
+Compare the models with `htmlreg()`. First the obesity models:
+```{r denver_obesity_summary, results="asis", eval=FALSE}
+denver_obesity_models <- list(denver_obese_sem, denver_obese_sem2, denver_obese_sdm, denver_obese_sdm2)
+names(denver_obesity_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
+                                rep(c("Base", "Parks")))
+htmlreg(denver_obesity_models, caption = "Denver: Models of Obesity Prevalence")
+```
+
+Next, the physical activity models:
+```{r denver_physact_summary, results="asis", eval=FALSE}
+denver_physact_models <- list(denver_physact_sem, denver_physact_sem2, denver_physact_sdm, denver_physact_sdm2)
+names(denver_physact_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
+                                rep(c("Base", "Parks")))
+htmlreg(denver_physact_models, caption = "Denver: Models of Physical Activity Participation")
+```
+
+And third, the mental health models:
+```{r denver_mental_summary, results="asis", eval=FALSE}
+denver_mental_models <- list(denver_mental_sem, denver_mental_sem2, denver_mental_sdm, denver_mental_sdm2)
+names(denver_mental_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
+                                rep(c("Base", "Parks")))
+htmlreg(denver_physact_models, caption = "Denver: Models of Variation in Self-Reported Mental Health")
+```
+
+## Boston
+```{r boston_models}
+
+```
+
+```{r bostonSDM_impacts}
+
+```
+
+##New York City
+```{r nyc_models}
+
+```
+
+```{r nycSDM_impacts}
+
+```
+
 # Discussion

### 2017-06-26 manuscript.Rmd
Switched Denver data source from GDB to geojson files

--- 2017-06-16 manuscript.Rmd
@@
 library(leaflet)
+library(tidyverse)
+library(spdep)
+library(maptools)
+library(rgdal)
+library(rgeos)
+library(texreg)
+library(leaflet)
 ```
@@
 ## Introduction
-
 This research will identify the correlation between size and access to urban parks, and physical activity, obesity and mental health at the neighborhood level.
@@
 
-##
+## Results
 Our anticipated results will assess the difference in physical activity and obesity at the neighborhood level when comparing proximity to parks and access to parks of various sizes and qualities as defined by park choice accessibility.
@@
 # Methods
-
 ```{r load_data}
@@
 
+## Denver
+
+Load Denver geospatial data (tracts and parks):
+```{r denver_data}
+
+#tracts <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_Final") 
+plot(denver_tracts)
+
+#parks <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_All_Parks") 
+plot(denver_parks)
+```
+
+Transform the attribute table into a tibble and select the relevant variables:
+```{r show_denverdata}
+denver_tracts@data <- tbl_df(tracts@data) %>%
+  select(GEOID_TRAC, OBESITY, Park_Percent, PhysAct, MENTAL, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegePercent, Pct0to17, Pct18to29, Pct30to64, Pct65plus, SinglePercent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic) %>%
+    mutate_each(funs(ifelse(is.na(.), 0, .)), Park_Percent)
+tracts@data
+```
+
+Calculate the logsum given the tracts and parks dataset:
+```{r denver_accessibility}
+source('R/size00001dist5.R', echo=TRUE)
+denver_tracts$park_ls <- calculate_park_logsums(denver_tracts, denver_parks, betas = c(.00001, -5))
+```
+
+Create regression equations for use in spatial econometric models:
+```{r denver_equations}
+denver_base_formula <- formula(~Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + CollegePercent + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + PctOther + PctHispanic)
+
+denver_parks_formula <- update(base_formula, . ~ . + park_ls)
+```
+
+Locate the centroid of all parks and all census tracts and create a distance matrix:
+```{r denver_distancematrix}
+tract_centroids <- gCentroid(denver_tracts, byid = TRUE) #if byid = FALSE, then centroid of "all" points
+park_centroids <- gCentroid(denver_parks, byid = TRUE)
+distance_matrix <- gDistance(tract_centroids, park_centroids, byid = TRUE)
+dim(distance_matrix)
+```
+
+Create a spatial weights matrix:
+```{r denver_W}
+neighbors <- poly2nb(denver_tracts, queen = FALSE)
+W <- nb2listw(neighbours = neighbors, zero.policy = TRUE)
+print(W, zero.policy = TRUE)
+```
+
+Estimate spatial econometric models for the `OBESITY` variable. The first model of each different type does not include `park_ls`:
+```{r denver_spmodels_obesity}
+denver_obese_sem <- errorsarlm(update(denver_base_formula, OBESITY ~ .), data = denver_tracts@data, 
+                      listw = W, zero.policy = TRUE)
+denver_obese_sem2 <- errorsarlm(update(denver_parks_formula, OBESITY ~ .), data = denver_tracts@data, 
+                      listw = W, zero.policy = TRUE)
+denver_obese_sdm <- lagsarlm(update(denver_base_formula, OBESITY ~ .), data = denver_tracts@data, 
+                      listw = W, zero.policy = TRUE, type = "mixed")
+denver_obese_sdm2 <- lagsarlm(update(denver_parks_formula, OBESITY ~ .), data = denver_tracts@data, 
+                      listw = W, zero.policy = TRUE, type = "mixed")
+```
+
+Estimate spatial econometric models for the `PhysAct` variable. The first model of each different type does not include `park_ls`:
+```{r denver_spmodels_physact}
+denver_physact_sem <- errorsarlm(update(denver_base_formula, PhysAct ~ .), data = denver_tracts@data, 
+                          listw = W, zero.policy = TRUE)
+denver_physact_sem2 <- errorsarlm(update(denver_parks_formula, PhysAct ~ .), 
+                           data = denver_tracts@data, listw = W, zero.policy = TRUE)
+denver_physact_sdm <- lagsarlm(update(denver_base_formula, PhysAct ~ .), data = denver_tracts@data, 
+                        listw = W, zero.policy = TRUE, type = "mixed")
+denver_physact_sdm2 <- lagsarlm(update(denver_parks_formula, PhysAct ~ .), data = denver_tracts@data,
+                         listw = W, zero.policy = TRUE, type = "mixed")
+```
+
+Estimate spatial econometric models for the `MENTAL` variable. The first model of each different type does not include `park_ls`:
+```{r denver_spmodels_mental}
+denver_mental_sem <- errorsarlm(update(denver_base_formula, MENTAL ~ .), data = denver_tracts@data, 
+                          listw = W, zero.policy = TRUE)
+denver_mental_sem2 <- errorsarlm(update(denver_parks_formula, MENTAL ~ .), 
+                           data = denver_tracts@data, listw = W, zero.policy = TRUE)
+denver_mental_sdm <- lagsarlm(update(denver_base_formula, MENTAL ~ .), data = denver_tracts@data, 
+                        listw = W, zero.policy = TRUE, type = "mixed")
+denver_mental_sdm2 <- lagsarlm(update(denver_parks_formula, MENTAL ~ .), data = denver_tracts@data,
+                         listw = W, zero.policy = TRUE, type = "mixed")
+```
+
+Calculate the impacts of the spatial durbin models:
+```{r denverSDM_impacts}
+listw <- as(W, "CsparseMatrix")
+tr_mult <- trW(listw, type="mult")
+tr_MC <- trW(listw, type="MC")
+set.seed(1)
+
+denver_noparks_obesemult <- impacts(denver_obese_sdm, tr=tr_mult)
+denver_parks_obesemult <- impacts(denver_obese_sdm2, tr=tr_mult)
+denver_noparks_obeseMC <- impacts(denver_obese_sdm, tr=tr_MC)
+denver_parks_obeseMC <- impacts(denver_obese_sdm2, tr=tr_MC)
+
+denver_noparks_physactmult <- impacts(denver_physact_sdm, tr=tr_mult)
+denver_parks_physactmult <- impacts(denver_physact_sdm2, tr=tr_mult)
+denver_noparks_physactMC <- impacts(denver_physact_sdm, tr=tr_MC)
+denver_parks_physactMC <- impacts(denver_physact_sdm2, tr=tr_MC)
+
+denver_noparks_mentalmult <- impacts(denver_mental_sdm, tr=tr_mult)
+denver_parks_mentalmult <- impacts(denver_mental_sdm2, tr=tr_mult)
+denver_noparks_mentalMC <- impacts(denver_mental_sdm, tr=tr_MC)
+denver_parks_mentalMC <- impacts(denver_mental_sdm2, tr=tr_MC)
+```
+
+Compare the models with `htmlreg()`. First the obesity models:
+```{r denver_obesity_summary, results="asis", eval=FALSE}
+denver_obesity_models <- list(denver_obese_sem, denver_obese_sem2, denver_obese_sdm, denver_obese_sdm2)
+names(denver_obesity_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
+                                rep(c("Base", "Parks")))
+htmlreg(denver_obesity_models, caption = "Denver: Models of Obesity Prevalence")
+```
+
+Next, the physical activity models:
+```{r denver_physact_summary, results="asis", eval=FALSE}
+denver_physact_models <- list(denver_physact_sem, denver_physact_sem2, denver_physact_sdm, denver_physact_sdm2)
+names(denver_physact_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
+                                rep(c("Base", "Parks")))
+htmlreg(denver_physact_models, caption = "Denver: Models of Physical Activity Participation")
+```
+
+And third, the mental health models:
+```{r denver_mental_summary, results="asis", eval=FALSE}
+denver_mental_models <- list(denver_mental_sem, denver_mental_sem2, denver_mental_sdm, denver_mental_sdm2)
+names(denver_mental_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
+                                rep(c("Base", "Parks")))
+htmlreg(denver_physact_models, caption = "Denver: Models of Variation in Self-Reported Mental Health")
+```
+
+## Boston
+```{r boston_models}
+
+```
+
+```{r bostonSDM_impacts}
+
+```
+
+##New York City
+```{r nyc_models}
+
+```
+
+```{r nycSDM_impacts}
+
+```
+
 # Discussion

### 2017-06-26 R/size00001dist5.R
Changed name to denver_size00001dist5

@@ -1,51 +1,0 @@
-#' Calculate destination choice accessibility logsum
-#' 
-#' @param size A vector of park sizes in acres
-#' @param distance A vector of distances to the parks in `size` in miles
-#' @param betas A vector containing the size and distance coefficients
-#'
-#' @return The accessibility logsum
-#' 
-park_logsum <- function(size, distance, betas = c(.00001, -5)){
-  
-  # calculate exponentiated utility of all parks
-  U <- betas[1] * size + betas[2] * distance 
-  eU <- exp(U)
-  
-  # log-sum
-  log(sum(eU))
-}
-
-
-#' Calculate destination choice logsums from a distance matrix
-#' 
-#' @param tracts A spatial points dataframe containing the 
-#'   tract geographic information and their attributes.
-#' @param parks A spatial points dataframe containing the 
-#'   park geographic information and their attributes.
-#' @param betas A vector containing the size and distance coefficients
-#'   
-#' @return An accessibility logsum calculation for each tract to every park.
-#' 
-calculate_park_logsums <- function(tracts, parks, betas = c(.00001, -5)){
-  
-  # calculate centroids of tracts and parks
-  tract_centroids <- gCentroid(tracts, byid = TRUE) 
-  park_centroids <- gCentroid(parks, byid = TRUE)
-  
-  # distances from all tracts to all zones
-  distances <- gDistance(park_centroids, tract_centroids, byid = TRUE) / 5280
-  
-  # vector containing park sizes 
-  park_sizes <- parks$Park_Acres
-  
-  # calculate observed utility 
-  #   beta_size * size + beta_distane * distance
-  V <- sweep(betas[2] * distances, MARGIN = 2, 
-             betas[1] * park_sizes, `+`)
-  
-  # log-sum of exponentiated utility
-  log(rowSums(exp(V)))
-  
-  
-}

### 2017-06-26 R/boston_size00001dist30.R
Uploaded Boston beta logsum calculation.

@@ -1,0 +1,51 @@
+#' Calculate destination choice accessibility logsum
+#' 
+#' @param size A vector of park sizes in acres
+#' @param distance A vector of distances to the parks in `size` in miles
+#' @param betas A vector containing the size and distance coefficients
+#'
+#' @return The accessibility logsum
+#' 
+park_logsum <- function(size, distance, betas = c(.00001, -30)){
+  
+  # calculate exponentiated utility of all parks
+  U <- betas[1] * size + betas[2] * distance 
+  eU <- exp(U)
+  
+  # log-sum
+  log(sum(eU))
+}
+
+
+#' Calculate destination choice logsums from a distance matrix
+#' 
+#' @param tracts A spatial points dataframe containing the 
+#'   tract geographic information and their attributes.
+#' @param parks A spatial points dataframe containing the 
+#'   park geographic information and their attributes.
+#' @param betas A vector containing the size and distance coefficients
+#'   
+#' @return An accessibility logsum calculation for each tract to every park.
+#' 
+calculate_park_logsums <- function(tracts, parks, betas = c(.00001, -30)){
+  
+  # calculate centroids of tracts and parks
+  tract_centroids <- gCentroid(tracts, byid = TRUE) 
+  park_centroids <- gCentroid(parks, byid = TRUE)
+  
+  # distances from all tracts to all zones
+  distances <- gDistance(park_centroids, tract_centroids, byid = TRUE) / 5280
+  
+  # vector containing park sizes 
+  park_sizes <- parks$Acreage
+  
+  # calculate observed utility 
+  #   beta_size * size + beta_distane * distance
+  V <- sweep(betas[2] * distances, MARGIN = 2, 
+             betas[1] * park_sizes, `+`)
+  
+  # log-sum of exponentiated utility
+  log(rowSums(exp(V)))
+  
+  
+}

### 2017-06-26 manuscript.Rmd
Added Boston analysis, including calculation of sdm impacts.

--- 2017-06-16 manuscript.Rmd
@@
 
+## Denver
+
+Plot Denver geospatial data (tracts and parks):
+```{r denver_data}
+
+#denver_tracts2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_Final") 
+plot(denver_tracts)
+
+#denver_parks2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_All_Parks") 
+plot(denver_parks)
+```
+
+Transform the attribute table into a tibble and select the relevant variables:
+```{r show_denverdata}
+denver_tracts@data <- tbl_df(tracts@data) %>%
+  select(GEOID_TRAC, OBESITY, Park_Percent, PhysAct, MENTAL, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegePercent, Pct0to17, Pct18to29, Pct30to64, Pct65plus, SinglePercent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic) %>%
+    mutate_each(funs(ifelse(is.na(.), 0, .)), Park_Percent)
+tracts@data
+```
+
+Calculate the logsum given the tracts and parks dataset:
+```{r denver_accessibility}
+source('R/denver_size00001dist5.R', echo=TRUE)
+denver_tracts$park_ls <- calculate_park_logsums(denver_tracts, denver_parks, betas = c(.00001, -5))
+```
+
+Create regression equations for use in spatial econometric models:
+```{r denver_equations}
+denver_base_formula <- formula(~Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + CollegePercent + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + PctOther + PctHispanic)
+
+denver_parks_formula <- update(base_formula, . ~ . + park_ls)
+```
+
+Locate the centroid of all parks and all census tracts and create a distance matrix:
+```{r denver_distancematrix}
+denver_tract_centroids <- gCentroid(denver_tracts, byid = TRUE) #if byid = FALSE, then centroid of "all" points
+denver_park_centroids <- gCentroid(denver_parks, byid = TRUE)
+distance_matrix <- gDistance(denver_tract_centroids, denver_park_centroids, byid = TRUE)
+dim(denver_distance_matrix)
+```
+
+Create a spatial weights matrix:
+```{r denver_W}
+denver_neighbors <- poly2nb(denver_tracts, queen = FALSE)
+denver_W <- nb2listw(neighbours = denver_neighbors, zero.policy = TRUE)
+print(denver_W, zero.policy = TRUE)
+```
+
+Estimate spatial econometric models for the `OBESITY` variable. The first model of each different type does not include `park_ls`:
+```{r denver_spmodels_obesity}
+denver_obese_sem <- errorsarlm(update(denver_base_formula, OBESITY ~ .), data = denver_tracts@data, 
+                      listw = denver_W, zero.policy = TRUE)
+denver_obese_sem2 <- errorsarlm(update(denver_parks_formula, OBESITY ~ .), data = denver_tracts@data, 
+                      listw = denver_W, zero.policy = TRUE)
+denver_obese_sdm <- lagsarlm(update(denver_base_formula, OBESITY ~ .), data = denver_tracts@data, 
+                      listw = denver_W, zero.policy = TRUE, type = "mixed")
+denver_obese_sdm2 <- lagsarlm(update(denver_parks_formula, OBESITY ~ .), data = denver_tracts@data, 
+                      listw = denver_W, zero.policy = TRUE, type = "mixed")
+```
+
+Estimate spatial econometric models for the `PhysAct` variable. The first model of each different type does not include `park_ls`:
+```{r denver_spmodels_physact}
+denver_physact_sem <- errorsarlm(update(denver_base_formula, PhysAct ~ .), data = denver_tracts@data, 
+                          listw = denver_W, zero.policy = TRUE)
+denver_physact_sem2 <- errorsarlm(update(denver_parks_formula, PhysAct ~ .), 
+                           data = denver_tracts@data, listw = denver_W, zero.policy = TRUE)
+denver_physact_sdm <- lagsarlm(update(denver_base_formula, PhysAct ~ .), data = denver_tracts@data, 
+                        listw = denver_W, zero.policy = TRUE, type = "mixed")
+denver_physact_sdm2 <- lagsarlm(update(denver_parks_formula, PhysAct ~ .), data = denver_tracts@data,
+                         listw = denver_W, zero.policy = TRUE, type = "mixed")
+```
+
+Estimate spatial econometric models for the `MENTAL` variable. The first model of each different type does not include `park_ls`:
+```{r denver_spmodels_mental}
+denver_mental_sem <- errorsarlm(update(denver_base_formula, MENTAL ~ .), data = denver_tracts@data, 
+                          listw = denver_W, zero.policy = TRUE)
+denver_mental_sem2 <- errorsarlm(update(denver_parks_formula, MENTAL ~ .), 
+                           data = denver_tracts@data, listw = denver_W, zero.policy = TRUE)
+denver_mental_sdm <- lagsarlm(update(denver_base_formula, MENTAL ~ .), data = denver_tracts@data, 
+                        listw = denver_W, zero.policy = TRUE, type = "mixed")
+denver_mental_sdm2 <- lagsarlm(update(denver_parks_formula, MENTAL ~ .), data = denver_tracts@data,
+                         listw = denver_W, zero.policy = TRUE, type = "mixed")
+```
+
+Calculate the impacts of the spatial durbin models:
+```{r denverSDM_impacts}
+denver_listw <- as(denver_W, "CsparseMatrix")
+denver_tr_mult <- trW(denver_listw, type="mult")
+denver_tr_MC <- trW(denver_listw, type="MC")
+set.seed(1)
+
+denver_noparks_obesemult <- impacts(denver_obese_sdm, tr=denver_tr_mult)
+denver_parks_obesemult <- impacts(denver_obese_sdm2, tr=denver_tr_mult)
+denver_noparks_obeseMC <- impacts(denver_obese_sdm, tr=denver_tr_MC)
+denver_parks_obeseMC <- impacts(denver_obese_sdm2, tr=denver_tr_MC)
+
+denver_noparks_physactmult <- impacts(denver_physact_sdm, tr=denver_tr_mult)
+denver_parks_physactmult <- impacts(denver_physact_sdm2, tr=denver_tr_mult)
+denver_noparks_physactMC <- impacts(denver_physact_sdm, tr=denver_tr_MC)
+denver_parks_physactMC <- impacts(denver_physact_sdm2, tr=denver_tr_MC)
+
+denver_noparks_mentalmult <- impacts(denver_mental_sdm, tr=denver_tr_mult)
+denver_parks_mentalmult <- impacts(denver_mental_sdm2, tr=denver_tr_mult)
+denver_noparks_mentalMC <- impacts(denver_mental_sdm, tr=denver_tr_MC)
+denver_parks_mentalMC <- impacts(denver_mental_sdm2, tr=denver_tr_MC)
+```
+
+Compare the models with `htmlreg()`. First the obesity models:
+```{r denver_obesity_summary, results="asis", eval=FALSE}
+denver_obesity_models <- list(denver_obese_sem, denver_obese_sem2, denver_obese_sdm, denver_obese_sdm2)
+names(denver_obesity_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
+                                rep(c("Base", "Parks")))
+htmlreg(denver_obesity_models, caption = "Denver: Models of Obesity Prevalence")
+```
+
+Next, the physical activity models:
+```{r denver_physact_summary, results="asis", eval=FALSE}
+denver_physact_models <- list(denver_physact_sem, denver_physact_sem2, denver_physact_sdm, denver_physact_sdm2)
+names(denver_physact_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
+                                rep(c("Base", "Parks")))
+htmlreg(denver_physact_models, caption = "Denver: Models of Physical Activity Participation")
+```
+
+And third, the mental health models:
+```{r denver_mental_summary, results="asis", eval=FALSE}
+denver_mental_models <- list(denver_mental_sem, denver_mental_sem2, denver_mental_sdm, denver_mental_sdm2)
+names(denver_mental_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
+                                rep(c("Base", "Parks")))
+htmlreg(denver_physact_models, caption = "Denver: Models of Variation in Self-Reported Mental Health")
+```
+
+## Boston
+
+Plot Boston geospatial data (tracts and parks):
+```{r boston_data}
+#boston_tracts2 <- readOGR(dsn = "data/Boston_Data.gdb", layer = "Boston_Final")
+plot(boston_tracts)
+
+#boston_parks2 <- readOGR(dsn = "data/Boston_Data.gdb", layer = "Boston_All_Parks") 
+plot(boston_parks)
+```
+
+Transform the attribute table into a tibble and select the relevant variables:
+```{r show_bostondata}
+tracts@data <- tbl_df(tracts@data) %>%
+  select(GEOID10, OBESITY, Phys_Act, MENTAL, Park_Percent, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegeDeg, Pct0to17, Pct18to29, Pct30to64, Pct65plus, SinglePercent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic)
+tracts@data
+```
+
+Calculate the logsum given the tracts and parks dataset:
+```{r boston_accessibility}
+source('boston_size00001dist30.R', echo=TRUE)
+boston_tracts$park_ls <- calculate_park_logsums(boston_tracts, boston_parks, betas = c(.00001, -30))
+```
+
+Create regression equations for use in spatial econometric models:
+```{r boston_equations}
+boston_base_formula <- formula(~Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + CollegeDeg + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + PctOther + PctHispanic)
+
+boston_parks_formula <- update(base_formula, . ~ . + park_ls)
+```
+
+Locate the centroid of all parks and all census tracts and create a distance matrix:
+```{r boston_distancematrix}
+boston_tract_centroids <- gCentroid(boston_tracts, byid = TRUE) #if byid = FALSE, then centroid of "all" points
+boston_park_centroids <- gCentroid(boston_parks, byid = TRUE)
+boston_distance_matrix <- gDistance(boston_tract_centroids, boston_park_centroids, byid = TRUE)
+dim(boston_distance_matrix)
+```
+
+Create a spatial weights matrix:
+```{r boston_W}
+boston_neighbors <- poly2nb(boston_tracts, queen = FALSE)
+boston_W <- nb2listw(neighbours = boston_neighbors, zero.policy = TRUE)
+print(boston_W, zero.policy = TRUE)
+```
+
+Estimate spatial econometric models for the `OBESITY` variable. The first model of each different type does not include `park_ls`:
+```{r boston_spmodels_obesity}
+boston_obese_sem <- errorsarlm(update(boston_base_formula, OBESITY ~ .), data = boston_tracts@data, 
+                      listw = boston_W, zero.policy = TRUE)
+boston_obese_sem2 <- errorsarlm(update(boston_parks_formula, OBESITY ~ .), data = boston_tracts@data, 
+                      listw = boston_W, zero.policy = TRUE)
+boston_obese_sdm <- lagsarlm(update(boston_base_formula, OBESITY ~ .), data = boston_tracts@data, 
+                      listw = boston_W, zero.policy = TRUE, type = "mixed")
+boston_obese_sdm2 <- lagsarlm(update(boston_parks_formula, OBESITY ~ .), data = boston_tracts@data, 
+                      listw = boston_W, zero.policy = TRUE, type = "mixed")
+```
+
+Estimate spatial econometric models for the `PhysAct` variable. The first model of each different type does not include `park_ls`:
+```{r boston_spmodels_physact}
+boston_physact_sem <- errorsarlm(update(boston_base_formula, Phys_Act ~ .), data = boston_tracts@data, 
+                          listw = boston_W, zero.policy = TRUE)
+boston_physact_sem2 <- errorsarlm(update(boston_parks_formula, Phys_Act ~ .), 
+                           data = boston_tracts@data, listw = boston_W, zero.policy = TRUE)
+boston_physact_sdm <- lagsarlm(update(boston_base_formula, Phys_Act ~ .), data = boston_tracts@data, 
+                        listw = boston_W, zero.policy = TRUE, type = "mixed")
+boston_physact_sdm2 <- lagsarlm(update(boston_parks_formula, Phys_Act ~ .), data = boston_tracts@data,
+                         listw = boston_W, zero.policy = TRUE, type = "mixed")
+```
+
+Estimate spatial econometric models for the `MENTAL` variable. The first model of each different type does not include `park_ls`:
+```{r boston_spmodels_mental}
+boston_mental_sem <- errorsarlm(update(boston_base_formula, MENTAL ~ .), data = boston_tracts@data, 
+                          listw = boston_W, zero.policy = TRUE)
+boston_mental_sem2 <- errorsarlm(update(boston_parks_formula, MENTAL ~ .), 
+                           data = boston_tracts@data, listw = boston_W, zero.policy = TRUE)
+boston_mental_sdm <- lagsarlm(update(boston_base_formula, MENTAL ~ .), data = boston_tracts@data, 
+                        listw = boston_W, zero.policy = TRUE, type = "mixed")
+boston_mental_sdm2 <- lagsarlm(update(boston_parks_formula, MENTAL ~ .), data = boston_tracts@data,
+                         listw = boston_W, zero.policy = TRUE, type = "mixed")
+```
+
+Calculate the impacts of the spatial durbin models:
+```{r bostonSDM_impacts}
+boston_listw <- as(boston_W, "CsparseMatrix")
+boston_tr_mult <- trW(boston_listw, type="mult")
+boston_tr_MC <- trW(boston_listw, type="MC")
+set.seed(1)
+
+boston_noparks_obesemult <- impacts(boston_obese_sdm, tr=boston_tr_mult)
+boston_parks_obesemult <- impacts(boston_obese_sdm2, tr=boston_tr_mult)
+boston_noparks_obeseMC <- impacts(boston_obese_sdm, tr=boston_tr_MC)
+boston_parks_obeseMC <- impacts(boston_obese_sdm2, tr=boston_tr_MC)
+
+boston_noparks_physactmult <- impacts(boston_physact_sdm, tr=boston_tr_mult)
+boston_parks_physactmult <- impacts(boston_physact_sdm2, tr=boston_tr_mult)
+boston_noparks_physactMC <- impacts(boston_physact_sdm, tr=boston_tr_MC)
+boston_parks_physactMC <- impacts(boston_physact_sdm2, tr=boston_tr_MC)
+
+boston_noparks_mentalmult <- impacts(boston_mental_sdm, tr=boston_tr_mult)
+boston_parks_mentalmult <- impacts(boston_mental_sdm2, tr=boston_tr_mult)
+boston_noparks_mentalMC <- impacts(boston_mental_sdm, tr=boston_tr_MC)
+boston_parks_mentalMC <- impacts(boston_mental_sdm2, tr=boston_tr_MC)
+```
+
+Compare the models with `htmlreg()`. First the obesity models:
+```{r boston_obesity_summary, results="asis", eval=FALSE}
+boston_obesity_models <- list(boston_obese_sem, boston_obese_sem2, boston_obese_sdm, boston_obese_sdm2)
+names(boston_obesity_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
+                                rep(c("Base", "Parks")))
+htmlreg(boston_obesity_models, caption = "Boston: Models of Obesity Prevalence")
+```
+
+Next, the physical activity models:
+```{r boston_physact_summary, results="asis", eval=FALSE}
+boston_physact_models <- list(boston_physact_sem, boston_physact_sem2, boston_physact_sdm, boston_physact_sdm2)
+names(boston_physact_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
+                                rep(c("Base", "Parks")))
+htmlreg(boston_physact_models, caption = "Boston: Models of Physical Activity Participation")
+```
+
+And third, the mental health models:
+```{r boston_mental_summary, results="asis", eval=FALSE}
+boston_mental_models <- list(boston_mental_sem, boston_mental_sem2, boston_mental_sdm, boston_mental_sdm2)
+names(boston_mental_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
+                                rep(c("Base", "Parks")))
+htmlreg(boston_physact_models, caption = "Boston: Models of Variation in Self-Reported Mental Health")
+```
+
+##New York City
+```{r nyc_models}
+
+```
+
 # Discussion

### 2017-06-26 R/nyc_size00001dist5.R
Uploaded NYC beta logsum calculation.

@@ -1,0 +1,51 @@
+#' Calculate destination choice accessibility logsum
+#' 
+#' @param size A vector of park sizes in acres
+#' @param distance A vector of distances to the parks in `size` in miles
+#' @param betas A vector containing the size and distance coefficients
+#'
+#' @return The accessibility logsum
+#' 
+park_logsum <- function(size, distance, betas = c(.00001, -5)){
+  
+  # calculate exponentiated utility of all parks
+  U <- betas[1] * size + betas[2] * distance 
+  eU <- exp(U)
+  
+  # log-sum
+  log(sum(eU))
+}
+
+
+#' Calculate destination choice logsums from a distance matrix
+#' 
+#' @param tracts A spatial points dataframe containing the 
+#'   tract geographic information and their attributes.
+#' @param parks A spatial points dataframe containing the 
+#'   park geographic information and their attributes.
+#' @param betas A vector containing the size and distance coefficients
+#'   
+#' @return An accessibility logsum calculation for each tract to every park.
+#' 
+calculate_park_logsums <- function(tracts, parks, betas = c(.00001, -5)){
+  
+  # calculate centroids of tracts and parks
+  tract_centroids <- gCentroid(tracts, byid = TRUE) 
+  park_centroids <- gCentroid(parks, byid = TRUE)
+  
+  # distances from all tracts to all zones
+  distances <- gDistance(park_centroids, tract_centroids, byid = TRUE) / 5280
+  
+  # vector containing park sizes 
+  park_sizes <- parks$Park_Acres
+  
+  # calculate observed utility 
+  #   beta_size * size + beta_distane * distance
+  V <- sweep(betas[2] * distances, MARGIN = 2, 
+             betas[1] * park_sizes, `+`)
+  
+  # log-sum of exponentiated utility
+  log(rowSums(exp(V)))
+  
+  
+}

### 2017-06-26 manuscript.Rmd
Added in NYC analysis, including calculation of SDM impacts.

@@
     mutate_each(funs(ifelse(is.na(.), 0, .)), Park_Percent)
-tracts@data
+denver_tracts@data
 ```
@@
   select(GEOID10, OBESITY, Phys_Act, MENTAL, Park_Percent, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegeDeg, Pct0to17, Pct18to29, Pct30to64, Pct65plus, SinglePercent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic)
-tracts@data
+boston_tracts@data
 ```
@@
 ```{r boston_accessibility}
-source('boston_size00001dist30.R', echo=TRUE)
+source('R/boston_size00001dist30.R', echo=TRUE)
 boston_tracts$park_ls <- calculate_park_logsums(boston_tracts, boston_parks, betas = c(.00001, -30))
@@
 ##New York City
-```{r nyc_models}
 
+Plot NYC geospatial data (tracts and parks):
+```{r nyc_data}
+#nyc_tracts2 <- readOGR(dsn = "data/NYC_Data.gdb", layer = "NYC_Final")
+plot(nyc_tracts)
+
+#nyc_parks2 <- readOGR(dsn = "data/NYC_Data.gdb", layer = "NYC_All_Parks") 
+plot(nyc_parks)
+```
+
+Transform the attribute table into a tibble and select the relevant variables: 
+```{r show_nycdata}
+nyc_tracts@data <- tbl_df(tracts@data) %>%
+  select(GEOID, OBESITY, Park_Percent, Phys_Act, MENTAL, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegeDeg, Pct0to17, Pct18to29, Pct30to64, Pct65plus, Single_Percent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic) %>%
+    mutate_each(funs(ifelse(is.na(.), 0, .)), Park_Percent)
+nyc_tracts@data
+```
+
+Calculate the logsum given a tracts and parks dataset:
+```{r nyc_accessibility}
+source('R/nyc_size00001dist5.R', echo=TRUE)
+nyc_tracts$park_ls <- calculate_park_logsums(nyc_tracts, nyc_parks, betas = c(.00001, -5))
+```
+
+Create regression equations for use in spatial econometric models:
+```{r nyc_equations}
+base_formula <- formula(~Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + CollegeDeg + Single_Percent + Pct0to17 + Pct18to29 + Pct30to64 + Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + PctOther + PctHispanic)
+
+parks_formula <- update(base_formula, . ~ . + park_ls)
+```
+
+Locate the centroid of all parks and all census tracts and create a distance matrix:
+```{r nyc_distancematrix}
+nyc_tract_centroids <- gCentroid(nyc_tracts, byid = TRUE) #if byid = FALSE, then centroid of "all" points
+nyc_park_centroids <- gCentroid(nyc_parks, byid = TRUE)
+nyc_distance_matrix <- gDistance(nyc_tract_centroids, nyc_park_centroids, byid = TRUE)
+dim(nyc_distance_matrix)
+```
+
+Create a spatial weights matrix:
+```{r nyc_W}
+nyc_neighbors <- poly2nb(nyc_tracts, queen = FALSE)
+nyc_W <- nb2listw(neighbours = nyc_neighbors, zero.policy = TRUE)
+print(nyc_W, zero.policy = TRUE)
+```
+
+Estimate spatial econometric models for the `OBESITY` variable. The first model of each different type does not include `park_ls`:
+```{r nyc_spmodels_obesity}
+nyc_obese_sem <- errorsarlm(update(nyc_base_formula, OBESITY ~ .), data = nyc_tracts@data, 
+                      listw = nyc_W, zero.policy = TRUE)
+nyc_obese_sem2 <- errorsarlm(update(nyc_parks_formula, OBESITY ~ .), data = nyc_tracts@data, 
+                      listw = nyc_W, zero.policy = TRUE)
+nyc_obese_sdm <- lagsarlm(update(nyc_base_formula, OBESITY ~ .), data = nyc_tracts@data, 
+                      listw = nyc_W, zero.policy = TRUE, type = "mixed")
+nyc_obese_sdm2 <- lagsarlm(update(nyc_parks_formula, OBESITY ~ .), data = nyc_tracts@data, 
+                      listw = nyc_W, zero.policy = TRUE, type = "mixed")
+```
+
+Estimate spatial econometric models for the `Phys_Act` variable. The first model of each different type does not include `park_ls`:
+```{r nyc_spmodels_physact}
+nyc_physact_sem <- errorsarlm(update(nyc_base_formula, Phys_Act ~ .), data = nyc_tracts@data, 
+                          listw = nyc_W, zero.policy = TRUE)
+nyc_physact_sem2 <- errorsarlm(update(nyc_parks_formula, Phys_Act ~ .), 
+                           data = nyc_tracts@data, listw = nyc_W, zero.policy = TRUE)
+nyc_physact_sdm <- lagsarlm(update(nyc_base_formula, Phys_Act ~ .), data = nyc_tracts@data, 
+                        listw = nyc_W, zero.policy = TRUE, type = "mixed")
+nyc_physact_sdm2 <- lagsarlm(update(nyc_parks_formula, Phys_Act ~ .), data = nyc_tracts@data,
+                         listw = nyc_W, zero.policy = TRUE, type = "mixed")
+```
+
+Estimate spatial econometric models for the `MENTAL` variable. The first model of each different type does not include `park_ls`:
+```{r nyc_spmodels_mental}
+nyc_mental_sem <- errorsarlm(update(nyc_base_formula, MENTAL ~ .), data = nyc_tracts@data, 
+                          listw = nyc_W, zero.policy = TRUE)
+nyc_mental_sem2 <- errorsarlm(update(nyc_parks_formula, MENTAL ~ .), 
+                           data = nyc_tracts@data, listw = nyc_W, zero.policy = TRUE)
+nyc_mental_sdm <- lagsarlm(update(nyc_base_formula, MENTAL ~ .), data = nyc_tracts@data, 
+                        listw = nyc_W, zero.policy = TRUE, type = "mixed")
+nyc_mental_sdm2 <- lagsarlm(update(nyc_parks_formula, MENTAL ~ .), data = nyc_tracts@data,
+                         listw = nyc_W, zero.policy = TRUE, type = "mixed")
+```
+
+Calculate the impacts of the spatial durbin models:
+```{r nycSDM_impacts}
+nyc_listw <- as(nyc_W, "CsparseMatrix")
+nyc_tr_mult <- trW(nyc_listw, type="mult")
+nyc_tr_MC <- trW(nyc_listw, type="MC")
+set.seed(1)
+
+nyc_noparks_obesemult <- impacts(nyc_obese_sdm, tr=nyc_tr_mult)
+nyc_parks_obesemult <- impacts(nyc_obese_sdm2, tr=nyc_tr_mult)
+nyc_noparks_obeseMC <- impacts(nyc_obese_sdm, tr=nyc_tr_MC)
+nyc_parks_obeseMC <- impacts(nyc_obese_sdm2, tr=nyc_tr_MC)
+
+nyc_noparks_physactmult <- impacts(nyc_physact_sdm, tr=nyc_tr_mult)
+nyc_parks_physactmult <- impacts(nyc_physact_sdm2, tr=nyc_tr_mult)
+nyc_noparks_physactMC <- impacts(nyc_physact_sdm, tr=nyc_tr_MC)
+nyc_parks_physactMC <- impacts(nyc_physact_sdm2, tr=nyc_tr_MC)
+
+nyc_noparks_mentalmult <- impacts(nyc_mental_sdm, tr=nyc_tr_mult)
+nyc_parks_mentalmult <- impacts(nyc_mental_sdm2, tr=nyc_tr_mult)
+nyc_noparks_mentalMC <- impacts(nyc_mental_sdm, tr=nyc_tr_MC)
+nyc_parks_mentalMC <- impacts(nyc_mental_sdm2, tr=nyc_tr_MC)
+```
+
+Compare the models with `htmlreg()`. First the obesity models:
+```{r nyc_obesity_summary, results="asis", eval=FALSE}
+nyc_obesity_models <- list(nyc_obese_sem, nyc_obese_sem2, nyc_obese_sdm, nyc_obese_sdm2)
+names(nyc_obesity_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
+                                rep(c("Base", "Parks")))
+htmlreg(nyc_obesity_models, caption = "NYC: Models of Obesity Prevalence")
+```
+
+Next, the physical activity models:
+```{r nyc_physact_summary, results="asis", eval=FALSE}
+nyc_physact_models <- list(nyc_physact_sem, nyc_physact_sem2, nyc_physact_sdm, nyc_physact_sdm2)
+names(nyc_physact_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
+                                rep(c("Base", "Parks")))
+htmlreg(nyc_physact_models, caption = "NYC: Models of Physical Activity Participation")
+```
+
+And third, the mental health models:
+```{r nyc_mental_summary, results="asis", eval=FALSE}
+nyc_mental_models <- list(nyc_mental_sem, nyc_mental_sem2, nyc_mental_sdm, nyc_mental_sdm2)
+names(nyc_mental_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
+                                rep(c("Base", "Parks")))
+htmlreg(nyc_physact_models, caption = "NYC: Models of Variation in Self-Reported Mental Health")
 ```

### 2017-06-30 manuscript.Rmd
Fixed NYC formatting.
Fixed errors that prevented R Markdown from knitting.

@@
 ```{r show_denverdata}
-denver_tracts@data <- tbl_df(tracts@data) %>%
+denver_tracts@data <- tbl_df(denver_tracts@data) %>%
   select(GEOID_TRAC, OBESITY, Park_Percent, PhysAct, MENTAL, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegePercent, Pct0to17, Pct18to29, Pct30to64, Pct65plus, SinglePercent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic) %>%
@@
 
-denver_parks_formula <- update(base_formula, . ~ . + park_ls)
+denver_parks_formula <- update(denver_base_formula, . ~ . + park_ls)
 ```
@@
 denver_park_centroids <- gCentroid(denver_parks, byid = TRUE)
-distance_matrix <- gDistance(denver_tract_centroids, denver_park_centroids, byid = TRUE)
+denver_distance_matrix <- gDistance(denver_tract_centroids, denver_park_centroids, byid = TRUE)
 dim(denver_distance_matrix)
@@
 ```{r show_bostondata}
-tracts@data <- tbl_df(tracts@data) %>%
+boston_tracts@data <- tbl_df(boston_tracts@data) %>%
   select(GEOID10, OBESITY, Phys_Act, MENTAL, Park_Percent, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegeDeg, Pct0to17, Pct18to29, Pct30to64, Pct65plus, SinglePercent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic)
@@
 
-boston_parks_formula <- update(base_formula, . ~ . + park_ls)
+boston_parks_formula <- update(boston_base_formula, . ~ . + park_ls)
 ```
@@
 
-##New York City
+## New York City
 
@@
 ```{r show_nycdata}
-nyc_tracts@data <- tbl_df(tracts@data) %>%
+nyc_tracts@data <- tbl_df(nyc_tracts@data) %>%
   select(GEOID, OBESITY, Park_Percent, Phys_Act, MENTAL, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegeDeg, Pct0to17, Pct18to29, Pct30to64, Pct65plus, Single_Percent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic) %>%
@@
 ```{r nyc_equations}
-base_formula <- formula(~Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + CollegeDeg + Single_Percent + Pct0to17 + Pct18to29 + Pct30to64 + Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + PctOther + PctHispanic)
+nyc_base_formula <- formula(~Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + CollegeDeg + Single_Percent + Pct0to17 + Pct18to29 + Pct30to64 + Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + PctOther + PctHispanic)
 
-parks_formula <- update(base_formula, . ~ . + park_ls)
+nyc_parks_formula <- update(nyc_base_formula, . ~ . + park_ls)
 ```

### 2017-07-14 manuscript.Rmd
Simplify and remove redundant code
I've used the lapply family of functions to loop over our dependent variables and our cities, so that we don't have to run every function 3 * 3 times.

--- 2017-06-26 manuscript.Rmd
@@
 library(leaflet)
+
+# source functions
+source("R/logsums.R")
+
+# variables
+cities <- c("denver", "boston", "nyc")
 ```
@@
 denver_tracts <- geojson_read("data/denver_tracts.geojson", what = "sp")
+denver_tracts$GEOID10 <- denver_tracts$GEOID_TRAC
 denver_parks <- geojson_read ("data/denver_parks.geojson", what = "sp")
@@
 nyc_parks <- geojson_read("data/nyc_parks.geojson", what = "sp")
+
+tract_shapes <- list(denver_tracts, boston_tracts, nyc_tracts)
+park_shapes <- list(denver_parks, boston_parks, nyc_parks)
 ```
@@
 Transform the attribute table into a tibble and select the relevant variables:
-```{r show_denverdata}
-denver_tracts@data <- tbl_df(tracts@data) %>%
-  select(GEOID_TRAC, OBESITY, Park_Percent, PhysAct, MENTAL, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegePercent, Pct0to17, Pct18to29, Pct30to64, Pct65plus, SinglePercent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic) %>%
-    mutate_each(funs(ifelse(is.na(.), 0, .)), Park_Percent)
-tracts@data
+```{r transformdata}
+#TODO: make sure all cities have the same data in the same names. It will save 
+# us LOTS of time
+# denver only, because the other cities have different variables
+regression_data <-
+  lapply(seq_along(1:1), function(i) {
+    tbl_df(tract_shapes[[i]]@data) %>%
+      mutate(
+        Park_Percent = ifelse(is.na(Park_Percent), 0, Park_Percent),
+        city = cities[i]
+      )
+  })
 ```
 
+DISCUSSION OF LOGSUM CALCULATION
+
 Calculate the logsum given the tracts and parks dataset:
-```{r denver_accessibility}
-source('R/denver_size00001dist5.R', echo=TRUE)
-denver_tracts$park_ls <- calculate_park_logsums(denver_tracts, denver_parks, betas = c(.00001, -5))
+```{r accessibility}
+regression_data[[1]]["park_ls"] <- calculate_park_logsums(
+  denver_tracts, denver_parks, betas = c(.00001, -5))
+regression_data[[2]]["park_ls"] <- calculate_park_logsums(
+  boston_tracts, boston_parks, betas = c(.00001, -30))
+regression_data[[1]]["park_ls"] <- calculate_park_logsums(
+  nyc_tracts, nyc_parks, betas = c(.00001, -5))
 ```
@@
 Create regression equations for use in spatial econometric models:
-```{r denver_equations}
-denver_base_formula <- formula(~Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + CollegePercent + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + PctOther + PctHispanic)
+```{r regression_eq}
+base_formula <- formula(
+  ~ Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + 
+    Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + 
+    CollegePercent + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + 
+    Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + 
+    PctOther + PctHispanic)
 
-denver_parks_formula <- update(base_formula, . ~ . + park_ls)
+parks_formula <- update(base_formula, . ~ . + park_ls)
 ```
@@
 Locate the centroid of all parks and all census tracts and create a distance matrix:
-```{r denver_distancematrix}
-denver_tract_centroids <- gCentroid(denver_tracts, byid = TRUE) #if byid = FALSE, then centroid of "all" points
-denver_park_centroids <- gCentroid(denver_parks, byid = TRUE)
-distance_matrix <- gDistance(denver_tract_centroids, denver_park_centroids, byid = TRUE)
-dim(denver_distance_matrix)
+```{r distancematrix}
+# why are we computing the distance matrices if we are using contiguity-based
+# neighbors?
+tract_centroids <- lapply(seq_along(1:length(cities)), function(i){
+  gCentroid(tract_shapes[[i]], byid = TRUE)
+})
+
+park_centroids <- lapply(seq_along(1:length(cities)), function(i){
+  gCentroid(park_shapes[[i]], byid = TRUE)
+})
+
+distance_matrices <- lapply(seq_along(1:length(cities)), function(i){
+  gDistance(tract_centroids[[i]], park_centroids[[i]], byid = TRUE)
+})
+
+names(distance_matrices) <- names(tract_centroids) <- names(park_centroids) <- cities
 ```
 
-Create a spatial weights matrix:
-```{r denver_W}
-denver_neighbors <- poly2nb(denver_tracts, queen = FALSE)
-denver_W <- nb2listw(neighbours = denver_neighbors, zero.policy = TRUE)
-print(denver_W, zero.policy = TRUE)
+```{r listw}
+list_ws <- lapply(seq_along(1:length(cities)), function(i){
+  nb <- poly2nb(tract_shapes[[i]], queen = FALSE)
+  nb2listw(neighbours = nb, zero.policy = TRUE)
+})
+names(list_ws) <- cities
 ```
 
-Estimate spatial econometric models for the `OBESITY` variable. The first model of each different type does not include `park_ls`:
-```{r denver_spmodels_obesity}
-denver_obese_sem <- errorsarlm(update(denver_base_formula, OBESITY ~ .), data = denver_tracts@data, 
-                      listw = denver_W, zero.policy = TRUE)
-denver_obese_sem2 <- errorsarlm(update(denver_parks_formula, OBESITY ~ .), data = denver_tracts@data, 
-                      listw = denver_W, zero.policy = TRUE)
-denver_obese_sdm <- lagsarlm(update(denver_base_formula, OBESITY ~ .), data = denver_tracts@data, 
-                      listw = denver_W, zero.policy = TRUE, type = "mixed")
-denver_obese_sdm2 <- lagsarlm(update(denver_parks_formula, OBESITY ~ .), data = denver_tracts@data, 
-                      listw = denver_W, zero.policy = TRUE, type = "mixed")
+Estimate spatial econometric models for the `OBESITY` variable. The first model
+of each different type does not include `park_ls`:
+
+```{r linear_models}
+# this lets us run all of the linear models (for all the cities) in like ten 
+# lines of code
+dependent_variables <- c("OBESITY", "PhysAct", "MENTAL")
+
+base_lm <- lapply(seq_along(1:length(dependent_variables)), function(i){
+
+  this_formula <- substitute(update(base_formula, x ~ .), 
+                             list(x = as.name(dependent_variables[i]) ))
+
+  bind_rows(regression_data) %>%
+    split(.$city) %>%
+    map(~lm(this_formula, data = .))
+})
+
+parks_lm <- lapply(seq_along(1:length(dependent_variables)), function(i){
+
+  this_formula <- substitute(update(parks_formula, x ~ .), 
+                             list(x = as.name(dependent_variables[i]) ))
+
+  bind_rows(regression_data) %>%
+    split(.$city) %>%
+    map(~lm(this_formula, data = .))
+})
+
+names(parks_lm) <- names(base_lm) <- dependent_variables
+# get a model with summary(base_lm$OBESITY$denver), for instance.
 ```
 
-Estimate spatial econometric models for the `PhysAct` variable. The first model of each different type does not include `park_ls`:
-```{r denver_spmodels_physact}
-denver_physact_sem <- errorsarlm(update(denver_base_formula, PhysAct ~ .), data = denver_tracts@data, 
-                          listw = denver_W, zero.policy = TRUE)
-denver_physact_sem2 <- errorsarlm(update(denver_parks_formula, PhysAct ~ .), 
-                           data = denver_tracts@data, listw = denver_W, zero.policy = TRUE)
-denver_physact_sdm <- lagsarlm(update(denver_base_formula, PhysAct ~ .), data = denver_tracts@data, 
-                        listw = denver_W, zero.policy = TRUE, type = "mixed")
-denver_physact_sdm2 <- lagsarlm(update(denver_parks_formula, PhysAct ~ .), data = denver_tracts@data,
-                         listw = denver_W, zero.policy = TRUE, type = "mixed")
+```{r sem}
+base_sem <- lapply(seq_along(1:length(dependent_variables)), function(dv){
+  this_formula <- substitute(update(base_formula, x ~ .), 
+                             list(x = as.name(dependent_variables[dv]) ))
+
+  # TODO update when more cities are available
+  models <- lapply(seq_along(1:1), function(city){
+    errorsarlm(this_formula, data = regression_data[[city]],
+               listw = list_ws[[city]], zero.policy = TRUE)
+  })
+
+  names(models) <- cities[1]
+  return(models)
+})
+
+park_sem <- lapply(seq_along(1:length(dependent_variables)), function(dv){
+  this_formula <- substitute(update(parks_formula, x ~ .), 
+                             list(x = as.name(dependent_variables[dv]) ))
+
+  # TODO update when more cities are available
+  models <- lapply(seq_along(1:1), function(city){
+    errorsarlm(this_formula, data = regression_data[[city]],
+               listw = list_ws[[city]], zero.policy = TRUE)
+  })
+
+  names(models) <- cities[1]
+  return(models)
+})
+
+names(park_sem) <- names(base_sem) <- dependent_variables
 ```
 
-Estimate spatial econometric models for the `MENTAL` variable. The first model of each different type does not include `park_ls`:
-```{r denver_spmodels_mental}
-denver_mental_sem <- errorsarlm(update(denver_base_formula, MENTAL ~ .), data = denver_tracts@data, 
-                          listw = denver_W, zero.policy = TRUE)
-denver_mental_sem2 <- errorsarlm(update(denver_parks_formula, MENTAL ~ .), 
-                           data = denver_tracts@data, listw = denver_W, zero.policy = TRUE)
-denver_mental_sdm <- lagsarlm(update(denver_base_formula, MENTAL ~ .), data = denver_tracts@data, 
-                        listw = denver_W, zero.policy = TRUE, type = "mixed")
-denver_mental_sdm2 <- lagsarlm(update(denver_parks_formula, MENTAL ~ .), data = denver_tracts@data,
-                         listw = denver_W, zero.policy = TRUE, type = "mixed")
+```{r sdm}
+base_sdm <- lapply(seq_along(1:length(dependent_variables)), function(dv){
+  this_formula <- substitute(update(base_formula, x ~ .), 
+                             list(x = as.name(dependent_variables[dv]) ))
+
+  # TODO update when more cities are available
+  models <- lapply(seq_along(1:1), function(city){
+    lagsarlm(this_formula, data = regression_data[[city]],
+             listw = list_ws[[city]], zero.policy = TRUE, type = "mixed")
+  })
+
+  names(models) <- cities[1]
+  return(models)
+})
+
+park_sdm <- lapply(seq_along(1:length(dependent_variables)), function(dv){
+  this_formula <- substitute(update(parks_formula, x ~ .), 
+                             list(x = as.name(dependent_variables[dv]) ))
+
+  # TODO update when more cities are available
+  models <- lapply(seq_along(1:1), function(city){
+    lagsarlm(this_formula, data = regression_data[[city]],
+             listw = list_ws[[city]], zero.policy = TRUE, type = "mixed")
+  })
+
+  names(models) <- cities[1]
+  return(models)
+})
+
+names(park_sdm) <- names(base_sdm) <- dependent_variables
 ```
@@
 Calculate the impacts of the spatial durbin models:
-```{r denverSDM_impacts}
-denver_listw <- as(denver_W, "CsparseMatrix")
-denver_tr_mult <- trW(denver_listw, type="mult")
-denver_tr_MC <- trW(denver_listw, type="MC")
-set.seed(1)
+```{r SDM_impacts}
+tr_mc <- lapply(list_ws, function(x){
+  trW(as(x, "CsparseMatrix"), type="MC")
+})
 
-denver_noparks_obesemult <- impacts(denver_obese_sdm, tr=denver_tr_mult)
-denver_parks_obesemult <- impacts(denver_obese_sdm2, tr=denver_tr_mult)
-denver_noparks_obeseMC <- impacts(denver_obese_sdm, tr=denver_tr_MC)
-denver_parks_obeseMC <- impacts(denver_obese_sdm2, tr=denver_tr_MC)
+mc_impacts <- lapply(base_sdm, function(dv){
+  # TODO
+  impacts <- lapply(seq_along(1:1), function(i) {
+    impacts(dv[[i]], tr = tr_mc[[i]])
+  })
 
-denver_noparks_physactmult <- impacts(denver_physact_sdm, tr=denver_tr_mult)
-denver_parks_physactmult <- impacts(denver_physact_sdm2, tr=denver_tr_mult)
-denver_noparks_physactMC <- impacts(denver_physact_sdm, tr=denver_tr_MC)
-denver_parks_physactMC <- impacts(denver_physact_sdm2, tr=denver_tr_MC)
+  names(impacts) <- cities[i]
 
-denver_noparks_mentalmult <- impacts(denver_mental_sdm, tr=denver_tr_mult)
-denver_parks_mentalmult <- impacts(denver_mental_sdm2, tr=denver_tr_mult)
-denver_noparks_mentalMC <- impacts(denver_mental_sdm, tr=denver_tr_MC)
-denver_parks_mentalMC <- impacts(denver_mental_sdm2, tr=denver_tr_MC)
+  return(impacts)
+})
+names(mc_impacts) <- dependent_variables
 ```
@@
 ```{r denver_obesity_summary, results="asis", eval=FALSE}
-denver_obesity_models <- list(denver_obese_sem, denver_obese_sem2, denver_obese_sdm, denver_obese_sdm2)
+denver_obesity_models <- list(
+  base_sem$OBESITY$denver, park_sem$OBESITY$denver,
+  base_sdm$OBESITY$denver, park_sdm$OBESITY$denver
+)
+
 names(denver_obesity_models) <- paste(rep(c("SEM", "SDM"), each = 2), 
                                       rep(c("Base", "Parks")))
+
 htmlreg(denver_obesity_models, caption = "Denver: Models of Obesity Prevalence")
@@
 ```{r denver_physact_summary, results="asis", eval=FALSE}
-denver_physact_models <- list(denver_physact_sem, denver_physact_sem2, denver_physact_sdm, denver_physact_sdm2)
+denver_physact_models <- list(
+  base_sem$PhysAct$denver, park_sem$PhysAct$denver,
+  base_sdm$PhysAct$denver, park_sdm$PhysAct$denver
+)
 names(denver_physact_models) <- paste(rep(c("SEM", "SDM"), each = 2),
@@
 And third, the mental health models:
-```{r denver_mental_summary, results="asis", eval=FALSE}
-denver_mental_models <- list(denver_mental_sem, denver_mental_sem2, denver_mental_sdm, denver_mental_sdm2)
-names(denver_mental_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
-                                rep(c("Base", "Parks")))
-htmlreg(denver_physact_models, caption = "Denver: Models of Variation in Self-Reported Mental Health")
-```
-
-## Boston
-
-Plot Boston geospatial data (tracts and parks):
-```{r boston_data}
-#boston_tracts2 <- readOGR(dsn = "data/Boston_Data.gdb", layer = "Boston_Final")
-plot(boston_tracts)
-
-#boston_parks2 <- readOGR(dsn = "data/Boston_Data.gdb", layer = "Boston_All_Parks") 
-plot(boston_parks)
-```
-
-Transform the attribute table into a tibble and select the relevant variables:
-```{r show_bostondata}
-tracts@data <- tbl_df(tracts@data) %>%
-  select(GEOID10, OBESITY, Phys_Act, MENTAL, Park_Percent, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegeDeg, Pct0to17, Pct18to29, Pct30to64, Pct65plus, SinglePercent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic)
-tracts@data
-```
-
-Calculate the logsum given the tracts and parks dataset:
-```{r boston_accessibility}
-source('boston_size00001dist30.R', echo=TRUE)
-boston_tracts$park_ls <- calculate_park_logsums(boston_tracts, boston_parks, betas = c(.00001, -30))
-```
-
-Create regression equations for use in spatial econometric models:
-```{r boston_equations}
-boston_base_formula <- formula(~Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + CollegeDeg + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + PctOther + PctHispanic)
-
-boston_parks_formula <- update(base_formula, . ~ . + park_ls)
-```
-
-Locate the centroid of all parks and all census tracts and create a distance matrix:
-```{r boston_distancematrix}
-boston_tract_centroids <- gCentroid(boston_tracts, byid = TRUE) #if byid = FALSE, then centroid of "all" points
-boston_park_centroids <- gCentroid(boston_parks, byid = TRUE)
-boston_distance_matrix <- gDistance(boston_tract_centroids, boston_park_centroids, byid = TRUE)
-dim(boston_distance_matrix)
-```
-
-Create a spatial weights matrix:
-```{r boston_W}
-boston_neighbors <- poly2nb(boston_tracts, queen = FALSE)
-boston_W <- nb2listw(neighbours = boston_neighbors, zero.policy = TRUE)
-print(boston_W, zero.policy = TRUE)
-```
-
-Estimate spatial econometric models for the `OBESITY` variable. The first model of each different type does not include `park_ls`:
-```{r boston_spmodels_obesity}
-boston_obese_sem <- errorsarlm(update(boston_base_formula, OBESITY ~ .), data = boston_tracts@data, 
-                      listw = boston_W, zero.policy = TRUE)
-boston_obese_sem2 <- errorsarlm(update(boston_parks_formula, OBESITY ~ .), data = boston_tracts@data, 
-                      listw = boston_W, zero.policy = TRUE)
-boston_obese_sdm <- lagsarlm(update(boston_base_formula, OBESITY ~ .), data = boston_tracts@data, 
-                      listw = boston_W, zero.policy = TRUE, type = "mixed")
-boston_obese_sdm2 <- lagsarlm(update(boston_parks_formula, OBESITY ~ .), data = boston_tracts@data, 
-                      listw = boston_W, zero.policy = TRUE, type = "mixed")
-```
-
-Estimate spatial econometric models for the `PhysAct` variable. The first model of each different type does not include `park_ls`:
-```{r boston_spmodels_physact}
-boston_physact_sem <- errorsarlm(update(boston_base_formula, Phys_Act ~ .), data = boston_tracts@data, 
-                          listw = boston_W, zero.policy = TRUE)
-boston_physact_sem2 <- errorsarlm(update(boston_parks_formula, Phys_Act ~ .), 
-                           data = boston_tracts@data, listw = boston_W, zero.policy = TRUE)
-boston_physact_sdm <- lagsarlm(update(boston_base_formula, Phys_Act ~ .), data = boston_tracts@data, 
-                        listw = boston_W, zero.policy = TRUE, type = "mixed")
-boston_physact_sdm2 <- lagsarlm(update(boston_parks_formula, Phys_Act ~ .), data = boston_tracts@data,
-                         listw = boston_W, zero.policy = TRUE, type = "mixed")
-```
-
-Estimate spatial econometric models for the `MENTAL` variable. The first model of each different type does not include `park_ls`:
-```{r boston_spmodels_mental}
-boston_mental_sem <- errorsarlm(update(boston_base_formula, MENTAL ~ .), data = boston_tracts@data, 
-                          listw = boston_W, zero.policy = TRUE)
-boston_mental_sem2 <- errorsarlm(update(boston_parks_formula, MENTAL ~ .), 
-                           data = boston_tracts@data, listw = boston_W, zero.policy = TRUE)
-boston_mental_sdm <- lagsarlm(update(boston_base_formula, MENTAL ~ .), data = boston_tracts@data, 
-                        listw = boston_W, zero.policy = TRUE, type = "mixed")
-boston_mental_sdm2 <- lagsarlm(update(boston_parks_formula, MENTAL ~ .), data = boston_tracts@data,
-                         listw = boston_W, zero.policy = TRUE, type = "mixed")
-```
-
-Calculate the impacts of the spatial durbin models:
-```{r bostonSDM_impacts}
-boston_listw <- as(boston_W, "CsparseMatrix")
-boston_tr_mult <- trW(boston_listw, type="mult")
-boston_tr_MC <- trW(boston_listw, type="MC")
-set.seed(1)
-
-boston_noparks_obesemult <- impacts(boston_obese_sdm, tr=boston_tr_mult)
-boston_parks_obesemult <- impacts(boston_obese_sdm2, tr=boston_tr_mult)
-boston_noparks_obeseMC <- impacts(boston_obese_sdm, tr=boston_tr_MC)
-boston_parks_obeseMC <- impacts(boston_obese_sdm2, tr=boston_tr_MC)
-
-boston_noparks_physactmult <- impacts(boston_physact_sdm, tr=boston_tr_mult)
-boston_parks_physactmult <- impacts(boston_physact_sdm2, tr=boston_tr_mult)
-boston_noparks_physactMC <- impacts(boston_physact_sdm, tr=boston_tr_MC)
-boston_parks_physactMC <- impacts(boston_physact_sdm2, tr=boston_tr_MC)
-
-boston_noparks_mentalmult <- impacts(boston_mental_sdm, tr=boston_tr_mult)
-boston_parks_mentalmult <- impacts(boston_mental_sdm2, tr=boston_tr_mult)
-boston_noparks_mentalMC <- impacts(boston_mental_sdm, tr=boston_tr_MC)
-boston_parks_mentalMC <- impacts(boston_mental_sdm2, tr=boston_tr_MC)
-```
-
-Compare the models with `htmlreg()`. First the obesity models:
-```{r boston_obesity_summary, results="asis", eval=FALSE}
-boston_obesity_models <- list(boston_obese_sem, boston_obese_sem2, boston_obese_sdm, boston_obese_sdm2)
-names(boston_obesity_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
-                                rep(c("Base", "Parks")))
-htmlreg(boston_obesity_models, caption = "Boston: Models of Obesity Prevalence")
-```
-
-Next, the physical activity models:
-```{r boston_physact_summary, results="asis", eval=FALSE}
-boston_physact_models <- list(boston_physact_sem, boston_physact_sem2, boston_physact_sdm, boston_physact_sdm2)
-names(boston_physact_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
-                                rep(c("Base", "Parks")))
-htmlreg(boston_physact_models, caption = "Boston: Models of Physical Activity Participation")
-```
-
-And third, the mental health models:
-```{r boston_mental_summary, results="asis", eval=FALSE}
-boston_mental_models <- list(boston_mental_sem, boston_mental_sem2, boston_mental_sdm, boston_mental_sdm2)
-names(boston_mental_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
-                                rep(c("Base", "Parks")))
-htmlreg(boston_physact_models, caption = "Boston: Models of Variation in Self-Reported Mental Health")
-```
-
-##New York City
-```{r nyc_models}
-
-```
 

### 2017-07-15 manuscript.Rmd
Fix impacts analysis
The impacts analysis relies on draws from the analytical Hessian matrix of the model. The problem is that the Hessian in spatial models is often close to singular, which means it cannot be inverted. spdep gets around this by using a numerical Hessian instead if the inversion fails (this is the warning that you get when you estimate the SDM).

The problem is that then the object that the impacts needs isn't there. So I've tightened the convergence tolerance on the estimation, and everything works. I've also added a helper function to process the impacts statistics in a bett

@@
 source("R/logsums.R")
+source("R/impact_summary.R")
 
@@
   boston_tracts, boston_parks, betas = c(.00001, -30))
-regression_data[[1]]["park_ls"] <- calculate_park_logsums(
+regression_data[[3]]["park_ls"] <- calculate_park_logsums(
   nyc_tracts, nyc_parks, betas = c(.00001, -5))
@@
     lagsarlm(this_formula, data = regression_data[[city]],
-             listw = list_ws[[city]], zero.policy = TRUE, type = "mixed")
+             listw = list_ws[[city]], zero.policy = TRUE, type = "mixed",
+             tol.solve = 1e-16)
   })
@@
   impacts <- lapply(seq_along(1:1), function(i) {
-    impacts(dv[[i]], tr = tr_mc[[i]])
+    impact_summary(summary(impacts(dv[[i]], tr = tr_mc[[i]], R = 500, empirical = TRUE)))
   })
 
-  names(impacts) <- cities[i]
+  names(impacts) <- cities[1]
 

### 2017-07-15 R/impact_summary.R

@@ -1,0 +1,28 @@
+#' Present impacts summary objects as a model matrix
+#' 
+#' @param sumimpacts An object created from summary(impacts(...))
+#' 
+impact_summary <- function(sumimpacts){
+  
+  effects <- c("total_sum", "direct_sum", "indirect_sum")
+  
+  outlist <- lapply(effects, function(effect){
+    coef <- sumimpacts[[effect]]$statistics[,1]
+    se <- sumimpacts[[effect]]$statistics[,2]
+    tstt <-  coef/se
+    pval <- 2 * (1 - pnorm(abs(tstt)))
+    
+    stars <- symnum(pval, corr = FALSE, na = FALSE, 
+                    cutpoints = c(0, 0.001, 0.01, 0.05, 0.1, 1), 
+                    symbols = c("^{***}", "^{**}", "^*", "^\\dagger", " "))
+    
+    coef_table <- cbind(coef, se, tstt, pval)
+    
+    list(coefTable = coef_table, stars = stars)
+  })
+  
+  names(outlist) <- effects
+  
+  return(outlist)
+  
+}

### 2017-07-17 manuscript.Rmd
Standardized variable names.

--- 2017-07-14 manuscript.Rmd
@@
 denver_tracts$GEOID10 <- denver_tracts$GEOID_TRAC
+denver_tracts$Phys_Act <- denver_tracts$PhysAct
+denver_tracts$CollegeDeg <- denver_tracts$CollegePercent
 denver_parks <- geojson_read ("data/denver_parks.geojson", what = "sp")
@@
 boston_parks <- geojson_read("data/boston_parks.geojson", what = "sp")
+boston_parks$Park_Acres <- boston_parks$Acreage
 
 nyc_tracts <- geojson_read("data/nyc_tracts.geojson", what = "sp")
+nyc_tracts$GEOID10 <- nyc_tracts$GEOID
+nyc_tracts$SinglePercent <- nyc_tracts$Single_Percent
 nyc_parks <- geojson_read("data/nyc_parks.geojson", what = "sp")

### 2017-07-19 manuscript.Rmd
Edits during the call with Kari

--- 2017-07-15 manuscript.Rmd
@@
 
+```{r}
+denver_plots <- spTransform(denver_tracts, CRSobj = CRS("+init=epsg:4326"))
+library(leaflet)
+leaflet() %>%
+  addTiles() %>%
+  addPolygons(data = denver_plots)
+```
+
 DISCUSSION OF LOGSUM CALCULATION
@@
   denver_tracts, denver_parks, betas = c(.00001, -5))
-regression_data[[2]]["park_ls"] <- calculate_park_logsums(
-  boston_tracts, boston_parks, betas = c(.00001, -30))
-regression_data[[3]]["park_ls"] <- calculate_park_logsums(
-  nyc_tracts, nyc_parks, betas = c(.00001, -5))
+# regression_data[[2]]["park_ls"] <- calculate_park_logsums(
+#   boston_tracts, boston_parks, betas = c(.00001, -30))
+# regression_data[[3]]["park_ls"] <- calculate_park_logsums(
+#   nyc_tracts, nyc_parks, betas = c(.00001, -5))
 ```
@@
 Create regression equations for use in spatial econometric models:
+
+We looked at income and it doesn't matter.
 ```{r regression_eq}
 base_formula <- formula(
-  ~ Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + 
-    Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + 
+  ~ log(Pop_Density) + FulltimeWork + 
     CollegePercent + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + 
@@
 Locate the centroid of all parks and all census tracts and create a distance matrix:
-```{r distancematrix}
+```{r distancematrix, eval = FALSE}
 # why are we computing the distance matrices if we are using contiguity-based
@@
 
-```{r sem}
+A likelihood ratio test of the SDM and SEM revealed that the SDM is more likely.
+
+```{r sem, eval = FALSE}
 base_sem <- lapply(seq_along(1:length(dependent_variables)), function(dv){
@@
 
-mc_impacts <- lapply(base_sdm, function(dv){
+mc_impacts <- lapply(park_sdm, function(dv){
   # TODO
@@
 
-htmlreg(denver_obesity_models, caption = "Denver: Models of Obesity Prevalence")
+screenreg(denver_obesity_models, caption = "Denver: Models of Obesity Prevalence")
 ```

### 2017-07-25 manuscript.Rmd
Standardized variable names according to Boston dataset and removed the Northeasternmost census tract from the Denver dataset.

@@
 ```{r load_data}
+# I've standardized the variable names based on the Boston dataset, so let's use those variable names moving forward.
+I also removed the Northeasternmost census tract from the Denver dataset as you suggested.
+
 denver_tracts <- geojson_read("data/denver_tracts.geojson", what = "sp")

### 2017-08-02 R/LogLikelihood_Comparison.Rmd
I went back to double check my tables of log likelihood values to make sure I hadn't entered anything incorrectly. As it turns out, I accidentally printed the physical activity models to htmlreg twice, which explains why the physical activity and mental health likelihood values were the same after adding park access into the models. I fixed the problem and added the correct values to the tables.
I removed the Northeastern census tract from Denver and also removed a handfull of census tracts from Boston that comprised mostly null values. As expected, the log likelihood values changed in Denver

@@
 author: "Nico Boyd"
-date: "June 19, 2017"
+date: "August 1, 2017"
 output:
@@
 
+  > It's more odd that the log-likelihoods are the same for both model before
+  the park access is added. Are you sure you didn't copy the wrong values/use the
+  wrong formula?
+
+  > *I went ahead and removed the large Northeastern census tract from Denver and also removed a handful of tracts      from Boston that comprised mostly null values.
+I re-ran the models and double checked myself but sure enough, the     log-likelihoods were the same for each set of models before adding park access.
+I discovered that the reason the log   likelihood values were the same for the physical activity and mental health models after adding park access was       that I had accidentally printed the physical activity model to htmlreg twice, so I fixed that problem and updated my   tables with the correct values.
+The results are less straightforward than what we saw before; see my notes below on   which models are most likely for each city and dependent variable.*
+
 Also, quick question about model selection: since the log likelihood values are all negative, should I or should I not select the final models based on the highest **ABSOLUTE VALUE** of the log likelihood?
@@
 
-  * Denver: models 1 & 4 (both equally likely)
-  * Boston: models 3 & 6 (both equally likely)
-  * NYC: models 1 & 2 (both equally likely)
+  > That's right; pick the least negative value.
 
-```{r denver_models, echo=FALSE}
+  * Denver: SEM models 1 & 4 are most likely (both equally so) for physical activity and mental health, but least         likely for obesity; SEM models 2 & 3 are tied for most likely for obesity.
+The same is true of the SDM models.
 
-Denver_Loglikelihoods <- data.frame(row.names=paste("Denver",1:6))
-Denver_Loglikelihoods[,1] <- c(-184.46, -184.46, -184.46, -184.46, -184.46, -184.46)
-Denver_Loglikelihoods[,2] <- c(-218.96, -218.96, -218.96, -218.96, -218.96, -218.96)
-Denver_Loglikelihoods[,3] <- c(-218.96, -218.96, -218.96, -218.96, -218.96, -218.96)
-Denver_Loglikelihoods[,4] <- c(-184.39, -184.43, -184.43, -184.39, -184.43, -184.43)
-Denver_Loglikelihoods[,5] <- c(-218.06, -218.28, -218.31, -218.06, -218.28, -218.31)
-Denver_Loglikelihoods[,6] <- c(-218.06, -218.28, -218.31, -218.06, -218.28, -218.31)
-colnames(Denver_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")
+  * Boston: SEM models 3 & 6 remain the most likely for all three dependent variables. However, for the SDM models, 1     & 3 are the most likely for all three variables.
 
-Denver_Loglikelihoods
+  * NYC: SEM models 1 & 2 are most likely for obesity and physical activity, while all three models are equally likely     for mental health.
+For the SDM models, model 3 is most likely for physical activity and mental health, but Model 1     is most likely for obesity.
+
+### Denver SEM Models
+Models 1 and 4 are the most likely (both equally so) for physical activity and mental health, but least likely for obesity.
+```{r denver_SEM_models, echo=FALSE}
+
+Denver_SEM_Loglikelihoods <- data.frame(row.names=paste("Denver",1:6))
+Denver_SEM_Loglikelihoods[,1] <- c(-183.33, -183.33, -183.33, -183.33, -183.33, -183.33)
+Denver_SEM_Loglikelihoods[,2] <- c(-216.98, -216.98, -216.98, -216.98, -216.98, -216.98)
+Denver_SEM_Loglikelihoods[,3] <- c(-134.84, -134.84, -134.84, -134.84, -134.84, -134.84)
+Denver_SEM_Loglikelihoods[,4] <- c(-183.16, -183.06, -183.06, -183.16, -183.06, -183.06)
+Denver_SEM_Loglikelihoods[,5] <- c(-216.86, -216.96, -216.97, -216.86, -216.96, -216.97)
+Denver_SEM_Loglikelihoods[,6] <- c(-134.67, -134.84, -134.84, -134.67, -134.84, -134.84)
+colnames(Denver_SEM_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")
+
+Denver_SEM_Loglikelihoods
 ```
 
-```{r boston_models, echo=FALSE}
+### Denver SDM Models
+Models 1 and 4 are most likely (both equally so) for physical activity and mental health, but least likely for obesity.
+```{r denver_SDM_models, echo=FALSE}
 
-Boston_Loglikelihoods <- data.frame(row.names=paste("Boston",1:6))
-Boston_Loglikelihoods[,1] <- c(-258.16, -258.16, -258.16, -258.16, -258.16, -258.16)
-Boston_Loglikelihoods[,2] <- c(-312.80, -312.80, -312.80, -312.80, -312.80, -312.80)
-Boston_Loglikelihoods[,3] <- c(-312.80, -312.80, -312.80, -312.80, -312.80, -312.80)
-Boston_Loglikelihoods[,4] <- c(-258.16, -258.16, -258.15, -258.16, -258.16, -258.15)
-Boston_Loglikelihoods[,5] <- c(-312.80, -312.79, -312.79, -312.80, -312.79, -312.79)
-Boston_Loglikelihoods[,6] <- c(-312.80, -312.79, -312.79, -312.80, -312.79, -312.79)
-colnames(Boston_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")
+Denver_SDM_Loglikelihoods <- data.frame(row.names=paste("Denver",1:6))
+Denver_SDM_Loglikelihoods[,1] <- c(-158.89, -158.89, -158.89, -158.89, -158.89, -158.89)
+Denver_SDM_Loglikelihoods[,2] <- c(-188.72, -188.72, -188.72, -188.72, -188.72, -188.72)
+Denver_SDM_Loglikelihoods[,3] <- c(-120.84, -120.84, -120.84, -120.84, -120.84, -120.84)
+Denver_SDM_Loglikelihoods[,4] <- c(-157.99, -158.54, -158.56, -157.99, -158.55, -158.56)
+Denver_SDM_Loglikelihoods[,5] <- c(-185.17, -185.29, -185.34, -185.17, -185.30, -185.34)
+Denver_SDM_Loglikelihoods[,6] <- c(-120.23, -120.64, -120.66, -120.23, -120.64, -120.66)
+colnames(Denver_SDM_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")
 
-Boston_Loglikelihoods
+Denver_SDM_Loglikelihoods
 ```
 
-```{r nyc_models, echo=FALSE}
+### Boston SEM Models
+Models 3 and 6 are most likely for all three dependent variables.
+```{r boston_SEM_models, echo=FALSE}
 
-NYC_Loglikelihoods <- data.frame(row.names=paste("NYC   ",1:3))
-NYC_Loglikelihoods[,1] <- c(-3929.85, -3929.85, -3929.85)
-NYC_Loglikelihoods[,2] <- c(-4421.83, -4421.83, -4421.83)
-NYC_Loglikelihoods[,3] <- c(-4421.83, -4421.83, -4421.83)
-NYC_Loglikelihoods[,4] <- c(-3929.14, -3929.14, -3929.36)
-NYC_Loglikelihoods[,5] <- c(-4421.80, -4421.80, -4421.82)
-NYC_Loglikelihoods[,6] <- c(-4421.80, -4421.80, -4421.82)
-colnames(NYC_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")
+Boston_SEM_Loglikelihoods <- data.frame(row.names=paste("Boston",1:6))
+Boston_SEM_Loglikelihoods[,1] <- c(-258.16, -258.16, -258.16, -258.16, -258.16, -258.16)
+Boston_SEM_Loglikelihoods[,2] <- c(-312.80, -312.80, -312.80, -312.80, -312.80, -312.80)
+Boston_SEM_Loglikelihoods[,3] <- c(-211.45, -211.45, -211.45, -211.45, -211.45, -211.45)
+Boston_SEM_Loglikelihoods[,4] <- c(-258.16, -258.16, -258.15, -258.16, -258.16, -258.15)
+Boston_SEM_Loglikelihoods[,5] <- c(-312.80, -312.79, -312.79, -312.80, -312.79, -312.79)
+Boston_SEM_Loglikelihoods[,6] <- c(-211.44, -211.43, -211.36, -211.44, -211.43, -211.36)
+colnames(Boston_SEM_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")
 
-NYC_Loglikelihoods
+Boston_SEM_Loglikelihoods
 ```
+
+### Boston SDM Models
+Models 1 and 3 are most likely for all three dependent variables.
+```{r boston_SDM_models, echo=FALSE}
+
+Boston_SDM_Loglikelihoods <- data.frame(row.names=paste("Boston",1:6))
+Boston_SDM_Loglikelihoods[,1] <- c(-230.37, -230.37, -230.37, -230.37, -230.37, -230.37)
+Boston_SDM_Loglikelihoods[,2] <- c(-298.10, -298.10, -298.10, -298.10, -298.10, -298.10)
+Boston_SDM_Loglikelihoods[,3] <- c(-198.01, -198.01, -198.01, -198.01, -198.01, -198.01)
+Boston_SDM_Loglikelihoods[,4] <- c(-228.51, -229.42, -229.87, -228.51, -229.42, -229.87)
+Boston_SDM_Loglikelihoods[,5] <- c(-297.21, -297.55, -297.73, -297.21, -297.55, -297.73)
+Boston_SDM_Loglikelihoods[,6] <- c(-197.19, -197.91, -197.74, -197.20, -197.91, -197.74)
+colnames(Boston_SDM_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")
+
+Boston_SDM_Loglikelihoods
+```
+
+### NYC SEM Models
+Models 1 and 2 are most likely (both equally so) for obesity and physical activity. All three models are equally likely for mental health.
+```{r nyc_SEM_models, echo=FALSE}
+
+NYC_SEM_Loglikelihoods <- data.frame(row.names=paste("NYC   ",1:3))
+NYC_SEM_Loglikelihoods[,1] <- c(-3929.85, -3929.85, -3929.85)
+NYC_SEM_Loglikelihoods[,2] <- c(-4421.83, -4421.83, -4421.83)
+NYC_SEM_Loglikelihoods[,3] <- c(-2716.36, -2716.36, -2716.36)
+NYC_SEM_Loglikelihoods[,4] <- c(-3929.14, -3929.14, -3929.36)
+NYC_SEM_Loglikelihoods[,5] <- c(-4421.80, -4421.80, -4421.82)
+NYC_SEM_Loglikelihoods[,6] <- c(-2716.33, -2716.33, -2716.33)
+colnames(NYC_SEM_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")
+
+NYC_SEM_Loglikelihoods
+```
+
+### NYC SDM Models
+Model 3 is most likely for physical activity and mental health, but Model 1 is most likely for obesity.
+```{r nyc_SDM_models, echo=FALSE}
+
+NYC_SDM_Loglikelihoods <- data.frame(row.names=paste("NYC   ",1:3))
+NYC_SDM_Loglikelihoods[,1] <- c(-3819.95, -3819.95, -3819.95)
+NYC_SDM_Loglikelihoods[,2] <- c(-4369.45, -4369.45, -4369.45)
+NYC_SDM_Loglikelihoods[,3] <- c(-2656.60, -2656.60, -2656.60)
+NYC_SDM_Loglikelihoods[,4] <- c(-3808.52, -3808.53, -3812.65)
+NYC_SDM_Loglikelihoods[,5] <- c(-4368.97, -4368.96, -4368.45)
+NYC_SDM_Loglikelihoods[,6] <- c(-2655.48, -2655.48, -2655.36)
+colnames(NYC_SDM_Loglikelihoods) <- c("Obesity_Noparks", "Physact_Noparks", "Mental_Noparks", "Obesity_Parks", "Physact_Parks", "Mental_Parks")
+
+NYC_SDM_Loglikelihoods
+```

### 2017-08-03 R/park_ls_analysis.Rmd
Ignore html.

---
title: "Park Access Analysis"
author: "Nico Boyd"
date: "August 2, 2017"
output: html_document
---

In this document I list the park_ls coefficient values for all models, indicate the presence or lack of significance, and note interesting findings that could become part of an overarching narrative in our paper.

# **Denver**

## **Denver 1** (size = .00001, distance = -5)

### Obesity Models
* OLS -> -0.05 (not significant)
* SAR -> -0.04 (not significant)
* SEM -> -0.05 (not significant)
* SDM -> +0.08 (not significant)  lag of park_ls = +0.19 (not significant)

### Physical Activity Models
* OLS -> +0.14 (not significant)
* SAR -> +0.14 (not significant)
* SEM -> +0.06 (not significant)
* SDM -> +0.23 (not significant)  lag of park_ls = +0.42 (**significant @ 0.01**)

  > *When my neighbors get better park access, I become less active. This model is one of the two most likely Spatial      Durbin models, the other being model 4.*

### Mental Health Models
* OLS -> +0.05 (not significant)
* SAR -> +0.05 (not significant)
* SEM -> +0.04 (not significant)
* SDM -> +0.06 (not significant)  lag of park_ls = +0.10 (not significant)

## **Denver 2** (size = .00001, distance = -15)

### Obesity Models
* OLS -> -0.02 (not significant)
* SAR -> -0.02 (not significant)
* SEM -> -0.02 (not significant)
* SDM -> +0.01 (not significant)  lag of park_ls = +0.04 (not significant)

### Physical Activity Models
* OLS -> +0.03 (not significant)
* SAR -> +0.03 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> +0.07 (not significant)  lag of park_ls = +0.14 (**significant at 0.05**)

   > *When my neighbors get better park access, I become less active.*

### Mental Health Models
* OLS -> +0.00 (not significant)
* SAR -> +0.00 (not significant)
* SEM -> +0.00 (not significant)
* SDM -> +0.01 (not significant)  lag of park_ls = +0.02 (not significant)

## **Denver 3** (size = .00001, distance = -30)

### Obesity Models
* OLS -> -0.01 (not significant)
* SAR -> -0.01 (not significant)
* SEM -> -0.01 (not significant)
* SDM -> +0.00 (not significant)  lag of park_ls = +0.02 (not significant)

### Physical Activity Models
* OLS -> +0.01 (not significant)
* SAR -> +0.02 (not significant)
* SEM -> +0.00 (not significant)
* SDM -> +0.03 (not significant)  lag of park_ls = +0.07 (**significant at 0.05**)

  > *When my neighbors get better park access, I become less physically active.*

### Mental Health Models
* OLS -> +0.00 (not significant)
* SAR -> +0.00 (not significant)
* SEM -> -0.00 (not significant)
* SDM -> +0.00 (not significant)  lag of park_ls = +0.01 (not significant)

## **Denver 4** (size = .0001, distance = -5)

### Obesity Models
* OLS -> -0.05 (not significant)
* SAR -> -0.04 (not significant)
* SEM -> -0.05 (not significant)
* SDM -> +0.08 (not significant)  lag of park_ls = +0.19 (not significant)

### Physical Activity Models
* OLS -> +0.14 (not significant)
* SAR -> +0.14 (not significant)
* SEM -> +0.06 (not significant)
* SDM -> +0.23 (**significant at 0.05**)  lag of park_ls = +0.42 (**significant at 0.05**)

  > *When I have better park access, I become less active. When my neighbors have better park access, I become even        less active. This model is one of the two most likely Spatial Durbin models, the other being model 1.*

### Mental Health Models
* OLS -> +0.05 (not significant)
* SAR -> +0.05 (not significant)
* SEM -> +0.04 (not significant)
* SDM -> +0.06 (not significant)  lag of park_ls = +0.10 (not significant)

## **Denver 5** (size = .0001, distance = -15)

### Obesity Models
* OLS -> -0.02 (not significant)
* SAR -> -0.02 (not significant)
* SEM -> -0.02 (not significant)
* SDM -> +0.01 (not significant)  lag of park_ls = +0.04 (not significant)

### Physical Activity Models
* OLS -> +0.03 (not significant)
* SAR -> +0.03 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> +0.07 (not significant)  lag of park_ls = +0.14 (**significant at 0.05**)

  > *When my neighbors have better park access, I become less active.*

### Mental Health Models
* OLS -> +0.00 (not significant)
* SAR -> +0.00 (not significant)
* SEM -> +0.00 (not significant)
* SDM -> +0.01 (not significant)  lag of park_ls = +0.02 (not significant)

## **Denver 6** (size = .0001, distance = -30)

### Obesity Models
* OLS -> -0.01 (not significant)
* SAR -> -0.01 (not significant)
* SEM -> -0.01 (not significant)
* SDM -> +0.00 (not significant)  lag of park_ls = +0.02 (not significant)

### Physical Activity Models
* OLS -> +0.01 (not significant)
* SAR -> +0.02 (not significant)
* SEM -> +0.00 (not significant)
* SDM -> +0.03 (not significant)  lag of park_ls = +0.07 (**significant at 0.05**)

  > *When my neighbors get better park access, I become less active.*

### Mental Health Models
* OLS -> +0.00 (not significant)
* SAR -> +0.00 (not significant)
* SEM -> -0.00 (not significant)
* SDM -> +0.00 (not significant)  lag of park_ls = +0.01 (not significant)

# **Boston**

## **Boston 1** (size = .00001, distance = -5)

### Obesity Models
* OLS -> +0.00 (not significant)
* SAR -> -0.04 (not significant)
* SEM -> -0.01 (not significant)
* SDM -> -0.30 (not significant)  lag of park_ls = -0.13 (not significant)

### Physical Activity Models
* OLS -> -0.03 (not significant)
* SAR -> -0.04 (not significant)
* SEM -> -0.02 (not significant)
* SDM -> -0.23 (not significant)  lag of park_ls = -0.26 (not significant)

### Mental Health Models
* OLS -> +0.04 (not significant)
* SAR -> +0.02 (not significant)
* SEM -> +0.02 (not significant)
* SDM -> -0.31 (not significant)  lag of park_ls = +0.31 (not significant)

## **Boston 2** (size = .00001, distance = -15)

### Obesity Models
* OLS -> +0.01 (not significant)
* SAR -> +0.00 (not significant)
* SEM -> +0.00 (not significant)
* SDM -> -0.08 (not significant)  lag of park_ls = -0.09 (not significant)

### Physical Activity Models
* OLS -> -0.02 (not significant)
* SAR -> -0.02 (not significant)
* SEM -> -0.02 (not significant)
* SDM -> -0.03 (not significant)  lag of park_ls = -0.19 (not significant)

### Mental Health Models
* OLS -> +0.02 (not significant)
* SAR -> +0.02 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> -0.01 (not significant)  lag of park_ls = +0.05 (not significant)

## **Boston 3** (size = .00001, distance = -30)

### Obesity Models
* OLS -> +0.01 (not significant)
* SAR -> +0.01 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> -0.03 (not significant)  lag of park_ls = -0.04 (not significant)

### Physical Activity Models
* OLS -> -0.01 (not significant)
* SAR -> -0.01 (not significant)
* SEM -> -0.01 (not significant)
* SDM -> -0.00 (not significant)  lag of park_ls = -0.09 (not significant)

### Mental Health Models
* OLS -> +0.02 (not significant)
* SAR -> +0.02 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> +0.02 (not significant)  lag of park_ls = +0.03 (not significant)

## **Boston 4** (size = .0001, distance = -5)

### Obesity Models
* OLS -> +0.00 (not significant)
* SAR -> -0.04 (not significant)
* SEM -> -0.01 (not significant)
* SDM -> -0.30 (not significant)  lag of park_ls = -0.13 (not significant)

### Physical Activity Models
* OLS -> -0.03 (not significant)
* SAR -> -0.04 (not significant)
* SEM -> -0.02 (not significant)
* SDM -> -0.23 (not significant)  lag of park_ls = -0.26 (not significant)

### Mental Health Models
* OLS -> +0.04 (not significant)
* SAR -> +0.02 (not significant)
* SEM -> +0.02 (not significant)
* SDM -> -0.31 (not significant)  lag of park_ls = +0.34 (not significant)

## **Boston 5** (size = .0001, distance = -15)

### Obesity Models
* OLS -> +0.01 (not significant)
* SAR -> +0.00 (not significant)
* SEM -> +0.00 (not significant)
* SDM -> -0.08 (not significant)  lag of park_ls = -0.09 (not significant)

### Physical Activity Models
* OLS -> -0.02 (not significant)
* SAR -> -0.02 (not significant)
* SEM -> -0.02 (not significant)
* SDM -> -0.03 (not significant)  lag of park_ls = -0.19 (not significant)

### Mental Health Models
* OLS -> +0.02 (not significant)
* SAR -> +0.02 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> -0.01 (not significant)  lag of park_ls = +0.05 (not significant)

## **Boston 6** (size = .0001, distance = -30)

### Obesity Models
* OLS -> +0.01 (not significant)
* SAR -> +0.01 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> -0.03 (not significant)  lag of park_ls = -0.04 (not significant)

### Physical Activity Models
* OLS -> -0.01 (not significant)
* SAR -> -0.01 (not significant)
* SEM -> -0.01 (not significant)
* SDM -> -0.00 (not significant)  lag of park_ls = -0.09 (not significant)

### Mental Health Models
* OLS -> +0.02 (not significant)
* SAR -> +0.02 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> +0.02 (not significant)  lag of park_ls = +0.03 (not significant)

# **NYC**

## **NYC 1** (size = .00001, distance = -5)

### Obesity Models
* OLS -> -0.74 (**significant at 0.001**)
* SAR -> -0.76 (**significant at 0.001**)
* SEM -> -0.12 (not significant)
* SDM -> +0.04 (not significant)  lag of park_ls = -0.43 (**significant at 0.001**)

  > *As my neighbors' park access decreases, I become more obese. Conversely, as my neighbors get better access to         parks, I become less obese. This spatial durbin model of obesity is the most likely in NYC.*

### Physical Activity Models
* OLS -> -0.05 (not significant)
* SAR -> -0.16 (not significant)
* SEM -> -0.02 (not significant)
* SDM -> +0.05 (not significant)  lag of park_ls = -0.15 (not significant)

### Mental Health Models
* OLS -> -0.01 (not significant)
* SAR -> -0.06 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> -0.08 (not significant)  lag of park_ls = +0.03 (not significant)

## **NYC 2** (size = .0001, distance = -5)

### Obesity Models
* OLS -> -0.74 (**significant at 0.001**)
* SAR -> -0.76 (**significant at 0.001**)
* SEM -> -0.12 (not significant)
* SDM -> +0.04 (not significant)  lag of park_ls = -0.43 (**significant at 0.01**)

  > *The OLS and SAR models indicate that I become less obese as my access to parks improves. The SDM model indicates      that as my neighbors get better access to parks, I become less obese.*

### Physical Activity Models
* OLS -> -0.05 (not significant)
* SAR -> -0.16 (not significant)
* SEM -> -0.02 (not significant)
* SDM -> +0.05 (not significant)  lag of park_ls = -0.15 (not significant)

### Mental Health Models
* OLS -> -0.01 (not significant)
* SAR -> -0.06 (not significant)
* SEM -> +0.01 (not significant)
* SDM -> -0.08 (not significant)  lag of park_ls = +0.03 (not significant)

## **NYC 3** (size = .00001, distance = -15)

### Obesity Models
* OLS -> -0.21 (**significant at 0.001**)
* SAR -> -0.21 (**significant at 0.001**)
* SEM -> -0.03 (not significant)
* SDM -> -0.03 (not significant)  lag of park_ls = -0.14 (**significant at 0.01**)

  > *The OLS and SAR models indicate that I become less obese as my access to parks improves. The SDM model indicates      that as my neighbors get better access to parks, I become less obese.*

### Physical Activity Models
* OLS -> -0.02 (not significant)
* SAR -> -0.04 (not significant)
* SEM -> -0.00 (not significant)
* SDM -> +0.01 (not significant)  lag of park_ls = -0.09 (not significant)

### Mental Health Models
* OLS -> -0.01 (not significant)
* SAR -> -0.02 (not significant)
* SEM -> -0.00 (not significant)
* SDM -> -0.02 (not significant)  lag of park_ls = -0.01 (not significant)

### 2017-08-03 manuscript.Rmd
Updated regression equation to Boston variable names.

@@
 output:
+  html_document: default
   pdf_document: default
-  html_document: default
 ---
@@
   denver_tracts, denver_parks, betas = c(.00001, -5))
-# regression_data[[2]]["park_ls"] <- calculate_park_logsums(
+#regression_data[[2]]["park_ls"] <- calculate_park_logsums(
  # boston_tracts, boston_parks, betas = c(.00001, -30))
-# regression_data[[3]]["park_ls"] <- calculate_park_logsums(
+#regression_data[[3]]["park_ls"] <- calculate_park_logsums(
  # nyc_tracts, nyc_parks, betas = c(.00001, -5))
@@
   ~ log(Pop_Density) + FulltimeWork + 
-    CollegePercent + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + 
+    CollegeDeg + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + 
     Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + 
@@
 # lines of code
-dependent_variables <- c("OBESITY", "PhysAct", "MENTAL")
+dependent_variables <- c("OBESITY", "Phys_Act", "MENTAL")
 
@@
 
-  names(models) <- cities[1]
+  names(models) <- cities[1:3]
   return(models)
@@
 denver_obesity_models <- list(
-  base_sem$OBESITY$denver, park_sem$OBESITY$denver,
-  base_sdm$OBESITY$denver, park_sdm$OBESITY$denver
+  #base_sem$OBESITY$denver, park_sem$OBESITY$denver,
+  base_sdm$OBESITY$denver, park_sdm$OBESITY$denver,
   )

### 2017-10-30 manuscript.Rmd
Updated links to parks datasets.

@@
 boston_tracts <- geojson_read("data/boston_tracts.geojson", what = "sp")
-boston_parks <- geojson_read("data/boston_parks.geojson", what = "sp")
+boston_parks <- geojson_read("data/boston_parks_final.geojson", what = "sp")
 boston_parks$Park_Acres <- boston_parks$Acreage
@@
 nyc_tracts$SinglePercent <- nyc_tracts$Single_Percent
-nyc_parks <- geojson_read("data/nyc_parks.geojson", what = "sp")
+nyc_parks <- geojson_read("data/nyc_parks_final.geojson", what = "sp")
 

### 2017-10-30 R/LogLikelihood_Comparison.Rmd
Updated log likelihood values after changing the parks dataset by removing private parks and sports stadiums.

@@
 Models 3 and 6 are most likely for all three dependent variables.
+(**These log likelihood values are not up to date but I am holding off on updating them because the park access coeffficient is not significant in any of the models**)
 ```{r boston_SEM_models, echo=FALSE}
@@
 Models 1 and 3 are most likely for all three dependent variables.
+(**These log likelihood values are not up to date but I am holding off on updating them because the park access coeffficient is not significant in any of the models**)
 ```{r boston_SDM_models, echo=FALSE}
@@
 NYC_SEM_Loglikelihoods[,3] <- c(-2716.36, -2716.36, -2716.36)
-NYC_SEM_Loglikelihoods[,4] <- c(-3929.14, -3929.14, -3929.36)
+NYC_SEM_Loglikelihoods[,4] <- c(-3929.15, -3929.15, -3929.38)
 NYC_SEM_Loglikelihoods[,5] <- c(-4421.80, -4421.80, -4421.82)
@@
 NYC_SDM_Loglikelihoods[,3] <- c(-2656.60, -2656.60, -2656.60)
-NYC_SDM_Loglikelihoods[,4] <- c(-3808.52, -3808.53, -3812.65)
-NYC_SDM_Loglikelihoods[,5] <- c(-4368.97, -4368.96, -4368.45)
+NYC_SDM_Loglikelihoods[,4] <- c(-3808.43, -3808.44, -3812.56)
+NYC_SDM_Loglikelihoods[,5] <- c(-4368.96, -4368.96, -4368.43)
 NYC_SDM_Loglikelihoods[,6] <- c(-2655.48, -2655.48, -2655.36)

### 2017-10-30 R/park_ls_analysis.Rmd
This document provides the park access coefficients and significance values for all models in all cities. I note the findings that I think seem important with the hope of identifying a strong narrative that we can use to frame our paper.
Updated park access coefficients based on new model runs with updated  park data.

@@
 author: "Nico Boyd"
-date: "August 2, 2017"
+date: "October 22, 2017"
 output: html_document
@@
 ### Obesity Models
-* OLS -> +0.00 (not significant)
-* SAR -> -0.04 (not significant)
-* SEM -> -0.01 (not significant)
-* SDM -> -0.30 (not significant)  lag of park_ls = -0.13 (not significant)
+* OLS -> +0.06 (not significant)
+* SAR -> +0.01 (not significant)
+* SEM -> +0.05 (not significant)
+* SDM -> -0.28 (not significant)  lag of park_ls = -0.12 (not significant)
 
 ### Physical Activity Models
-* OLS -> -0.03 (not significant)
-* SAR -> -0.04 (not significant)
-* SEM -> -0.02 (not significant)
-* SDM -> -0.23 (not significant)  lag of park_ls = -0.26 (not significant)
+* OLS -> +0.00 (not significant)
+* SAR -> -0.02 (not significant)
+* SEM -> +0.01 (not significant)
+* SDM -> -0.24 (not significant)  lag of park_ls = -0.28 (not significant)
 
 ### Mental Health Models
-* OLS -> +0.04 (not significant)
-* SAR -> +0.02 (not significant)
-* SEM -> +0.02 (not significant)
-* SDM -> -0.31 (not significant)  lag of park_ls = +0.31 (not significant)
+* OLS -> +0.08 (not significant)
+* SAR -> +0.06 (not significant)
+* SEM -> +0.06 (not significant)
+* SDM -> -0.21 (not significant)  lag of park_ls = +0.24 (not significant)
 
@@
 ### Obesity Models
-* OLS -> +0.01 (not significant)
-* SAR -> +0.00 (not significant)
-* SEM -> +0.00 (not significant)
-* SDM -> -0.08 (not significant)  lag of park_ls = -0.09 (not significant)
+* OLS -> +0.03 (not significant)
+* SAR -> +0.02 (not significant)
+* SEM -> +0.02 (not significant)
+* SDM -> -0.09 (not significant)  lag of park_ls = -0.07 (not significant)
 
 ### Physical Activity Models
-* OLS -> -0.02 (not significant)
-* SAR -> -0.02 (not significant)
-* SEM -> -0.02 (not significant)
-* SDM -> -0.03 (not significant)  lag of park_ls = -0.19 (not significant)
+* OLS -> -0.03 (not significant)
+* SAR -> -0.03 (not significant)
+* SEM -> -0.03 (not significant)
+* SDM -> -0.05 (not significant)  lag of park_ls = -0.17 (not significant)
 
@@
 * OLS -> +0.02 (not significant)
-* SAR -> +0.02 (not significant)
+* SAR -> +0.01 (not significant)
 * SEM -> +0.01 (not significant)
@@
 ### Obesity Models
-* OLS -> +0.01 (not significant)
+* OLS -> +0.02 (not significant)
 * SAR -> +0.01 (not significant)
 * SEM -> +0.01 (not significant)
-* SDM -> -0.03 (not significant)  lag of park_ls = -0.04 (not significant)
+* SDM -> -0.04 (not significant)  lag of park_ls = -0.03 (not significant)
 
@@
 * SEM -> -0.01 (not significant)
-* SDM -> -0.00 (not significant)  lag of park_ls = -0.09 (not significant)
+* SDM -> -0.00 (not significant)  lag of park_ls = -0.08 (not significant)
 
 ### Mental Health Models
-* OLS -> +0.02 (not significant)
-* SAR -> +0.02 (not significant)
-* SEM -> +0.01 (not significant)
-* SDM -> +0.02 (not significant)  lag of park_ls = +0.03 (not significant)
+* OLS -> +0.01 (not significant)
+* SAR -> +0.01 (not significant)
+* SEM -> +0.00 (not significant)
+* SDM -> +0.00 (not significant)  lag of park_ls = +0.03 (not significant)
 
@@
 ### Obesity Models
-* OLS -> +0.00 (not significant)
-* SAR -> -0.04 (not significant)
-* SEM -> -0.01 (not significant)
-* SDM -> -0.30 (not significant)  lag of park_ls = -0.13 (not significant)
+* OLS -> +0.06 (not significant)
+* SAR -> +0.01 (not significant)
+* SEM -> +0.05 (not significant)
+* SDM -> -0.28 (not significant)  lag of park_ls = -0.12 (not significant)
 
 ### Physical Activity Models
-* OLS -> -0.03 (not significant)
-* SAR -> -0.04 (not significant)
-* SEM -> -0.02 (not significant)
-* SDM -> -0.23 (not significant)  lag of park_ls = -0.26 (not significant)
+* OLS -> +0.00 (not significant)
+* SAR -> -0.02 (not significant)
+* SEM -> +0.01 (not significant)
+* SDM -> -0.24 (not significant)  lag of park_ls = -0.28 (not significant)
 
 ### Mental Health Models
-* OLS -> +0.04 (not significant)
-* SAR -> +0.02 (not significant)
-* SEM -> +0.02 (not significant)
-* SDM -> -0.31 (not significant)  lag of park_ls = +0.34 (not significant)
+* OLS -> +0.08 (not significant)
+* SAR -> +0.06 (not significant)
+* SEM -> +0.06 (not significant)
+* SDM -> -0.21 (not significant)  lag of park_ls = +0.24 (not significant)
 
@@
 ### Obesity Models
+* OLS -> +0.02 (not significant)
+* SAR -> +0.01 (not significant)
+* SEM -> +0.01 (not significant)
+* SDM -> -0.04 (not significant)  lag of park_ls = -0.03 (not significant)
+
+### Physical Activity Models
+* OLS -> -0.02 (not significant)
+* SAR -> -0.02 (not significant)
+* SEM -> -0.02 (not significant)
+* SDM -> -0.02 (not significant)  lag of park_ls = -0.08 (not significant)
+
+### Mental Health Models
 * OLS -> +0.01 (not significant)
 * SAR -> +0.01 (not significant)
-* SEM -> +0.01 (not significant)
-* SDM -> -0.03 (not significant)  lag of park_ls = -0.04 (not significant)
-
-### Physical Activity Models
-* OLS -> -0.01 (not significant)
-* SAR -> -0.01 (not significant)
-* SEM -> -0.01 (not significant)
-* SDM -> -0.00 (not significant)  lag of park_ls = -0.09 (not significant)
-
-### Mental Health Models
-* OLS -> +0.02 (not significant)
-* SAR -> +0.02 (not significant)
-* SEM -> +0.01 (not significant)
-* SDM -> +0.02 (not significant)  lag of park_ls = +0.03 (not significant)
+* SEM -> +0.00 (not significant)
+* SDM -> +0.00 (not significant)  lag of park_ls = +0.03 (not significant)
 
@@
 * SEM -> -0.12 (not significant)
-* SDM -> +0.04 (not significant)  lag of park_ls = -0.43 (**significant at 0.001**)
+* SDM -> +0.04 (not significant)  lag of park_ls = -0.43 (**significant at 0.05**)
 
-  > *As my neighbors' park access decreases, I become more obese.
+  > *The OLS and SAR models indicate that as my access to parks improves, I become less obese.
+According to the SDM model, as my neighbors' park access decreases, I become more obese.
 Conversely, as my neighbors get better access to parks, I become less obese.
@@
 * SEM -> -0.02 (not significant)
-* SDM -> +0.05 (not significant)  lag of park_ls = -0.15 (not significant)
+* SDM -> +0.05 (**significant at 0.001**)  lag of park_ls = -0.15 (not significant)
+
+> *The SDM model indicates that I become less active as my access to parks improves.*
 
@@
 * SEM -> +0.01 (not significant)
-* SDM -> -0.08 (not significant)  lag of park_ls = +0.03 (not significant)
+* SDM -> -0.08 (**significant at 0.001**)  lag of park_ls = +0.03 (not significant)
+
+> *The SDM model indicates that my self-reported mental health becomes better as my access to parks improves.*
 
@@
 * SEM -> -0.12 (not significant)
-* SDM -> +0.04 (not significant)  lag of park_ls = -0.43 (**significant at 0.01**)
+* SDM -> +0.04 (not significant)  lag of park_ls = -0.43 (not significant)
 
-  > *The OLS and SAR models indicate that I become less obese as my access to parks improves. The SDM model indicates      that as my neighbors get better access to parks, I become less obese.*
+  > *The OLS and SAR models indicate that I become less obese as my access to parks improves.*
 
@@
 * OLS -> -0.05 (not significant)
-* SAR -> -0.16 (not significant)
+* SAR -> -0.16 (**significant at 0.05**)
 * SEM -> -0.02 (not significant)
 * SDM -> +0.05 (not significant)  lag of park_ls = -0.15 (not significant)
+
+> *The SAR model indicates that I become less obese as my access to parks improves.*
 

### 2017-11-02 manuscript.Rmd
Added new lines of code that allowed me to check the impacts for Boston and NYC.

@@
 cities <- c("denver", "boston", "nyc")
+#cities <- c("boston", "denver", "nyc")
+#cities <- c("nyc", "boston", "denver")
 ```
@@
 
+## I removed the really large Northeasternmost census tracts from Boston as well as a number of private parks. I also removed professional sports stadiums from the NYC parks dataset.
+
 denver_tracts <- geojson_read("data/denver_tracts.geojson", what = "sp")
@@
 
+#tract_shapes <- list (boston_tracts, denver_tracts, nyc_tracts)
 tract_shapes <- list(denver_tracts, boston_tracts, nyc_tracts)
+#tract_shapes <- list(nyc_tracts, boston_tracts, denver_tracts)
+#park_shapes <- list(boston_parks, denver_parks, nyc_parks)
 park_shapes <- list(denver_parks, boston_parks, nyc_parks)
+#park_shapes <- list(nyc_parks, boston_parks, denver_parks)
 ```
@@
 #denver_tracts2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_Final") 
+#plot(boston_tracts)
 plot(denver_tracts)
+#plot(nyc_tracts)
 
 #denver_parks2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_All_Parks") 
+#plot(boston_parks)
 plot(denver_parks)
+#plot(nyc_parks)
 ```
@@
 ```{r}
+#boston_plots <- spTransform(boston_tracts, CRSobj = CRS("+init=epsg:4326"))
 denver_plots <- spTransform(denver_tracts, CRSobj = CRS("+init=epsg:4326"))
+#nyc_plots <- spTransform(nyc_tracts, CRSobj = CRS("+init=epsg:4326"))
 library(leaflet)
@@
   addTiles() %>%
+  #addPolygons(data = nyc_plots)
   addPolygons(data = denver_plots)
+  #addPolygons(data = boston_plots)
 ```
@@
 regression_data[[1]]["park_ls"] <- calculate_park_logsums(
-  denver_tracts, denver_parks, betas = c(.00001, -5))
+  denver_tracts, denver_parks, betas = c(.00001, -15))
+#regression_data[[1]]["park_ls"] <- calculate_park_logsums(
+  #boston_tracts, boston_parks, betas = c(.00001, -5))
+#regression_data[[1]]["park_ls"] <- calculate_park_logsums(
+  #nyc_tracts, nyc_parks, betas = c(.00001, -15))
 #regression_data[[2]]["park_ls"] <- calculate_park_logsums(
@@
 
-  names(models) <- cities[1:3]
+  names(models) <- cities[1:1]
   return(models)

### 2017-12-19 manuscript.Rmd
Made some small additions to the code to allow me to run the analysis for all three cities instead of just Denver alone.

--- 2017-10-30 manuscript.Rmd
@@
 # variables
-cities <- c("denver", "boston", "nyc")
+#cities <- c("denver", "boston", "nyc")
+cities <- c("boston", "denver", "nyc")
+#cities <- c("nyc", "boston", "denver")
 ```
@@
 
-tract_shapes <- list(denver_tracts, boston_tracts, nyc_tracts)
-park_shapes <- list(denver_parks, boston_parks, nyc_parks)
+tract_shapes <- list (boston_tracts, denver_tracts, nyc_tracts)
+#tract_shapes <- list(denver_tracts, boston_tracts, nyc_tracts)
+#tract_shapes <- list(nyc_tracts, boston_tracts, denver_tracts)
+park_shapes <- list(boston_parks, denver_parks, nyc_parks)
+#park_shapes <- list(denver_parks, boston_parks, nyc_parks)
+#park_shapes <- list(nyc_parks, boston_parks, denver_parks)
 ```
@@
 #denver_tracts2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_Final") 
-plot(denver_tracts)
+plot(boston_tracts)
+#plot(denver_tracts)
+#plot(nyc_tracts)
 
 #denver_parks2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_All_Parks") 
-plot(denver_parks)
+plot(boston_parks)
+#plot(denver_parks)
+#plot(nyc_parks)
 ```
@@
 ```{r}
-denver_plots <- spTransform(denver_tracts, CRSobj = CRS("+init=epsg:4326"))
+boston_plots <- spTransform(boston_tracts, CRSobj = CRS("+init=epsg:4326"))
+#denver_plots <- spTransform(denver_tracts, CRSobj = CRS("+init=epsg:4326"))
+#nyc_plots <- spTransform(nyc_tracts, CRSobj = CRS("+init=epsg:4326"))
 library(leaflet)
@@
   addTiles() %>%
-  addPolygons(data = denver_plots)
+  #addPolygons(data = nyc_plots)
+  #addPolygons(data = denver_plots)
+  addPolygons(data = boston_plots)
 ```
@@
 ```{r accessibility}
+#regression_data[[1]]["park_ls"] <- calculate_park_logsums(
+  #denver_tracts, denver_parks, betas = c(.00001, -15))
 regression_data[[1]]["park_ls"] <- calculate_park_logsums(
-  denver_tracts, denver_parks, betas = c(.00001, -5))
+  boston_tracts, boston_parks, betas = c(.00001, -5))
+#regression_data[[1]]["park_ls"] <- calculate_park_logsums(
+  #nyc_tracts, nyc_parks, betas = c(.00001, -15))
 #regression_data[[2]]["park_ls"] <- calculate_park_logsums(

### 2018-01-05 manuscript.Rmd
Enable all three cities in Rmarkdown evaluation

--- 2017-10-30 manuscript.Rmd
@@
 
+knitr::opts_chunk$set(cache = TRUE)
+
 # source functions
@@
 # variables
-cities <- c("denver", "boston", "nyc")
+cities <- c("boston", "denver", "nyc")
 ```
@@
 
-tract_shapes <- list(denver_tracts, boston_tracts, nyc_tracts)
-park_shapes <- list(denver_parks, boston_parks, nyc_parks)
+tract_shapes <- list (boston_tracts, denver_tracts, nyc_tracts)
+park_shapes <- list(boston_parks, denver_parks, nyc_parks)
 ```
@@
 regression_data <-
-  lapply(seq_along(1:1), function(i) {
+  lapply(seq_along(1:length(cities)), function(i) {
     tbl_df(tract_shapes[[i]]@data) %>%
@@
 ```{r}
+boston_plots <- spTransform(boston_tracts, CRSobj = CRS("+init=epsg:4326"))
 denver_plots <- spTransform(denver_tracts, CRSobj = CRS("+init=epsg:4326"))
+nyc_plots <- spTransform(nyc_tracts, CRSobj = CRS("+init=epsg:4326"))
 library(leaflet)
@@
 ```{r accessibility}
-regression_data[[1]]["park_ls"] <- calculate_park_logsums(
-  denver_tracts, denver_parks, betas = c(.00001, -5))
-#regression_data[[2]]["park_ls"] <- calculate_park_logsums(
- # boston_tracts, boston_parks, betas = c(.00001, -30))
-#regression_data[[3]]["park_ls"] <- calculate_park_logsums(
- # nyc_tracts, nyc_parks, betas = c(.00001, -5))
+betas <- list(
+  boston = c(0.00001, -30), 
+  denver = c(0.00001, -15), 
+  nyc = c(0.0001, -5)
+)
+for(i in 1:length(cities)){
+  regression_data[[i]]["park_ls"] <- calculate_park_logsums(
+    tract_shapes[[i]], park_shapes[[i]], betas = betas[[i]])
+}
 ```
@@
 
-  # TODO update when more cities are available
-  models <- lapply(seq_along(1:1), function(city){
+  models <- lapply(seq_along(1:length(cities)), function(city){
     errorsarlm(this_formula, data = regression_data[[city]],
@@
 
-  names(models) <- cities[1]
+  names(models) <- cities
   return(models)
@@
 
-  # TODO update when more cities are available
-  models <- lapply(seq_along(1:1), function(city){
+  models <- lapply(seq_along(1:length(cities)), function(city){
     lagsarlm(this_formula, data = regression_data[[city]],
@@
 
-  names(models) <- cities[1:3]
+  names(models) <- cities
   return(models)
@@
 mc_impacts <- lapply(park_sdm, function(dv){
-  # TODO
-  impacts <- lapply(seq_along(1:1), function(i) {
+  impacts <- lapply(seq_along(1:length(cities)), function(i) {
     impact_summary(summary(impacts(dv[[i]], tr = tr_mc[[i]], R = 500, empirical = TRUE)))
@@
 
-  names(impacts) <- cities[1]
+  names(impacts) <- cities
 
@@
 denver_obesity_models <- list(
-  #base_sem$OBESITY$denver, park_sem$OBESITY$denver,
-  base_sdm$OBESITY$denver, park_sdm$OBESITY$denver,
+  base_sdm$OBESITY$denver, park_sdm$OBESITY$denver
   )
 
-names(denver_obesity_models) <- paste(rep(c("SEM", "SDM"), each = 2), 
+names(denver_obesity_models) <- paste(rep(c("SDM"), each = 2), 
                                       rep(c("Base", "Parks")))
@@
 denver_physact_models <- list(
-  base_sem$PhysAct$denver, park_sem$PhysAct$denver,
-  base_sdm$PhysAct$denver, park_sdm$PhysAct$denver
+  base_sem$Phys_Act$denver, park_sem$Phys_Act$denver,
+  base_sdm$Phys_Act$denver, park_sdm$Phys_Act$denver
 )
@@
                                       rep(c("Base", "Parks")))
-htmlreg(denver_physact_models, caption = "Denver: Models of Physical Activity Participation")
+screenreg(denver_physact_models, caption = "Denver: Models of Physical Activity Participation")
 ```

### 2018-01-05 manuscript.Rmd
Cache manuscript during rmarkdown creation

@@
 
-```{r setup}
+```{r setup, cache = FALSE, warning = FALSE, message = FALSE}
 library(geojsonio)

### 2018-01-05 manuscript.Rmd
Add discussion of log-sum calculation

@@
 
-# Results
+Consider that an individual is choosing a park for a recreation activity.
+According to basic choice theory (Mcfadden 1974), the probability of choosing
+park $i$ from the set of all regional parks $P$ is:
 
-## Denver
+$$ P(i | V_i) = \frac{\exp(V_i)}{\sum_{j \in P}\exp(V_j)}$$
+where parks are differentiated from each other by their relative measurable
+utilitie $V$. In principle, $V$ may include any measurable attributes of either
+the choice maker or the park. In this study we use an elementary linear formulation of
 
-Plot Denver geospatial data (tracts and parks):
-```{r denver_data}
+$$V_i = \beta_a acreage + \beta_d distance$$
+incorporating the size of the park in acres and the distance of the park from
+each census tract in miles. The coefficients $\beta$ are typically estimated from 
+surveys, though in the absence of a survey we apply a maximum likelihood
+technique described below.
 
-#denver_tracts2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_Final") 
-plot(boston_tracts)
-#plot(denver_tracts)
-#plot(nyc_tracts)
+A key theoretical understanding of random utility choice models is that the
+consumer surplus of the choice set can be otained as the log-sum of the
+denominator of the choice probability equation. In plainer terms, the *total value*
+of an individual's park accessibility is defined to be:
 
-#denver_parks2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_All_Parks") 
-plot(boston_parks)
-#plot(denver_parks)
-#plot(nyc_parks)
-```
+$$\ln\left({\sum_{j \in P}\exp(V_j)}\right)$$
 
-Transform the attribute table into a tibble and select the relevant variables:
+There are several advantages to a log-sum defined metric relative to
+buffer-based accessibility metrics more commonly found in the literature. First,
+all individuals are defined as having some access to all parks, rather than an
+arbitrary limit of 1/2 mile or so. This allows for the fact that some people are
+more or less sensitive to distances, and that distance is a continuous, and not
+a binary, phenomenon. Second, the random utility formulation allows the
+researcher to include any attribute of the park; in this case, we consider the
+size of the park as an element of accessibility. This suggests that not all
+parks are equal, and that a large park such as New York City's Central Park may
+provide health and activity benefits over a much larger area than a smaller
+community square.
+
+McFadden, D. (1974). The measurement of urban travel demand. Journal of public economics, 3(4), 303-328.
+
+In the absence of a park choice survey, we estimated likely values of the $\beta$ 
+coefficients by iteratively searching for the values which produced the highest
+model likelihood in *which model did we use to estimate likelihood?*. The search
+was constrained by two assertions. First, we required that the coefficient on
+size be positive and that on distance negative; all else equal, people will
+prefer to use larger parks that are nearer to their residence. Second, we visually
+inspected the resulting accessibility scores to ensure that the scores produced a 
+reasonably varied pattern of access throughout the metropolitan region.
+
 ```{r transformdata}
@@
 
-```{r}
+```{r city_plots, eval = FALSE}
 boston_plots <- spTransform(boston_tracts, CRSobj = CRS("+init=epsg:4326"))
@@
 
-DISCUSSION OF LOGSUM CALCULATION
-
-Calculate the logsum given the tracts and parks dataset:
-```{r accessibility}
+```{r betas}
 betas <- list(
@@
 )
+```
+
+Calculate the logsum given the tracts and parks dataset:
+```{r accessibility}
 for(i in 1:length(cities)){
@@
 
+# Results
 Create regression equations for use in spatial econometric models:
-
 We looked at income and it doesn't matter.
